### 2020-10-26 chaloupka_sameshima_wallner_final_project.Rmd
initial commit

---
title: "Final Project"
author: "Ben Chaloupka, Tess Sameshima, and Scott Wallner"
date: "10/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 2020-11-10 raw_dwell_times.Rmd
add new rmd
rmd includes raw dwell time data and graphical representations of the raw data

---
title: "fractal_data_raw"
author: "sgwallner"
date: "11/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rio)
library(here)

```

```{r}

raw_A <- import("frac_SA.csv")

raw_B <- import("frac_SB.csv")
```

```{r}
raw_A_long <- raw_A %>% 
 pivot_longer(cols = a:f, names_to = "participant", values_to = "dwell_time")

raw_B_long <- raw_B %>% 
 pivot_longer(cols = g:p, names_to = "participant", values_to = "dwell_time")
```

```{r}
raw_A_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

raw_B_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

raw_A_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_line()

raw_B_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_line()

raw_A_long %>% 
  ggplot(aes(x = number, y = dwell_time)) +
  facet_wrap("participant") +
  geom_line() +
  geom_smooth(mehthod = "lm", se = F)

raw_B_long %>% 
  ggplot(aes(x = number, y = dwell_time)) +
  facet_wrap("participant") +
  geom_line() +
  geom_smooth(mehthod = "lm", se = F)
```

# it would be good to try these analyses again with the outliers removed
# can we normalize the data
# put in pictures with tab pills, GIF would be cool
# significant difference between images
# significant difference between sequence position

### 2020-11-11 raw_dwell_times.Rmd
add notes to raw times
suggested additional analyses

@@
 
-# it would be good to try these analyses again with the outliers removed
+# try these analyses again with the outliers removed
 # can we normalize the data
@@
 # significant difference between sequence position
+# present each participants most and least viewed
+# compare most and least viewed by sequence position

### 2020-11-16 chaloupka_sameshima_wallner_final_project.Rmd
Class on 11/16
Finalize Data Draft Script

@@
 knitr::opts_chunk$set(echo = TRUE)
+
+library(here)
+library(rio)
+library(janitor)
+library(tidyverse)
+
+theme_set(theme_minimal())
 ```
+
+## Import Data
+
+```{r import_data}
+fractal_data <- clean_names(import(here("data", "frac_total.csv")))
+
+raw_A <- clean_names(import(here("data", "frac_SA.csv")))
+
+raw_B <- clean_names(import(here("data", "frac_SB.csv")))
+```
+
+## Clean Data
+
+```{r clean_data}
+fractal_data <- fractal_data %>% 
+  pivot_longer(cols = a:p,
+               names_to = "participant",
+               values_to = "dwell_time")
+
+fractal_data <- fractal_data %>% 
+  mutate(direction = factor(direction, labels = c("Decay", "Growth", "Random")),
+         participant = factor(participant),
+         disp_image = factor(disp_image))
+
+fractal_data <- fractal_data %>% 
+  mutate(fractal_type = case_when(
+    grepl("Fern_A", disp_image, fixed = T) ~ "Fern_A",
+    grepl("Fern_B", disp_image, fixed = T) ~ "Fern_B",
+    grepl("Fractal_Curves_A", disp_image, fixed = T) ~ "Fractal_Curves_A",
+    grepl("Fractal_Curves_B", disp_image, fixed = T) ~ "Fractal_Curves_B",
+    grepl("Fractal_Curves_C", disp_image, fixed = T) ~ "Fractal_Curves_C",
+    grepl("Fractal_Curves_D", disp_image, fixed = T) ~ "Fractal_Curves_D",
+    grepl("Fractal_Curves_E", disp_image, fixed = T) ~ "Fractal_Curves_E",
+    grepl("Hilbert", disp_image, fixed = T) ~ "Hilbert",
+    grepl("Moore", disp_image, fixed = T) ~ "Moore",
+    grepl("Pythagoras_A", disp_image, fixed = T) ~ "Pythagoras_A",
+    grepl("Pythagoras_B", disp_image, fixed = T) ~ "Pythagoras_B",
+    grepl("Sierpinski_A", disp_image, fixed = T) ~ "Sierpinski_A",
+    grepl("Sierpinski_B", disp_image, fixed = T) ~ "Sierpinski_B",
+    grepl("Tree_A", disp_image, fixed = T) ~ "Tree_A"
+  ))
+
+fractal_data <- fractal_data %>% 
+  mutate(sequence_position = case_when(
+    grepl("A0.png", disp_image, fixed = T) ~ 1,
+    grepl("B0.png", disp_image, fixed = T) ~ 1,
+    grepl("C0.png", disp_image, fixed = T) ~ 1,
+    grepl("D0.png", disp_image, fixed = T) ~ 1,
+    grepl("E0.png", disp_image, fixed = T) ~ 1,
+    grepl("_0.png", disp_image, fixed = T) ~ 1,
+    grepl("A100.png", disp_image, fixed = T) ~ 2,
+    grepl("B100.png", disp_image, fixed = T) ~ 2,
+    grepl("A1.png", disp_image, fixed = T) ~ 2,
+    grepl("B1.png", disp_image, fixed = T) ~ 2,
+    grepl("C1.png", disp_image, fixed = T) ~ 2,
+    grepl("D1.png", disp_image, fixed = T) ~ 2,
+    grepl("E1.png", disp_image, fixed = T) ~ 2,
+    grepl("_1.png", disp_image, fixed = T) ~ 2,
+    grepl("A200.png", disp_image, fixed = T) ~ 3,
+    grepl("B200.png", disp_image, fixed = T) ~ 3,
+    grepl("A2.png", disp_image, fixed = T) ~ 3,
+    grepl("B2.png", disp_image, fixed = T) ~ 3,
+    grepl("C2.png", disp_image, fixed = T) ~ 3,
+    grepl("D2.png", disp_image, fixed = T) ~ 3,
+    grepl("E2.png", disp_image, fixed = T) ~ 3,
+    grepl("_2.png", disp_image, fixed = T) ~ 3,
+    grepl("A400.png", disp_image, fixed = T) ~ 4,
+    grepl("B400.png", disp_image, fixed = T) ~ 4,
+    grepl("A3.png", disp_image, fixed = T) ~ 4,
+    grepl("B3.png", disp_image, fixed = T) ~ 4,
+    grepl("C3.png", disp_image, fixed = T) ~ 4,
+    grepl("D3.png", disp_image, fixed = T) ~ 4,
+    grepl("E3.png", disp_image, fixed = T) ~ 4,
+    grepl("_3.png", disp_image, fixed = T) ~ 4,
+    grepl("A800.png", disp_image, fixed = T) ~ 5,
+    grepl("B800.png", disp_image, fixed = T) ~ 5,
+    grepl("A4.png", disp_image, fixed = T) ~ 5,
+    grepl("B4.png", disp_image, fixed = T) ~ 5,
+    grepl("C4.png", disp_image, fixed = T) ~ 5,
+    grepl("D4.png", disp_image, fixed = T) ~ 5,
+    grepl("E4.png", disp_image, fixed = T) ~ 5,
+    grepl("_4.png", disp_image, fixed = T) ~ 5,
+    grepl("A1600.png", disp_image, fixed = T) ~ 6,
+    grepl("B1600.png", disp_image, fixed = T) ~ 6,
+    grepl("A5.png", disp_image, fixed = T) ~ 6,
+    grepl("B5.png", disp_image, fixed = T) ~ 6,
+    grepl("C5.png", disp_image, fixed = T) ~ 6,
+    grepl("D5.png", disp_image, fixed = T) ~ 6,
+    grepl("E5.png", disp_image, fixed = T) ~ 6,
+    grepl("_5.png", disp_image, fixed = T) ~ 6,
+    grepl("A3200.png", disp_image, fixed = T) ~ 7,
+    grepl("B3200.png", disp_image, fixed = T) ~ 7,
+    grepl("A6.png", disp_image, fixed = T) ~ 7,
+    grepl("A6400.png", disp_image, fixed = T) ~ 8,
+    grepl("B6400.png", disp_image, fixed = T) ~ 8,
+    grepl("A7.png", disp_image, fixed = T) ~ 8,
+    grepl("A12800.png", disp_image, fixed = T) ~ 9,
+    grepl("B12800.png", disp_image, fixed = T) ~ 9
+  ))
+
+raw_A_long <- raw_A %>% 
+ pivot_longer(cols = a:f, names_to = "participant", values_to = "dwell_time")
+
+raw_B_long <- raw_B %>% 
+ pivot_longer(cols = g:p, names_to = "participant", values_to = "dwell_time")
+```
+
+## Create New Dataset Excluding Outliers
+
+```{r}
+cutoff <- mean(fractal_data$dwell_time) + 3 * sd(fractal_data$dwell_time)
+
+filtered_fractal_data <- fractal_data %>% 
+  filter(dwell_time < cutoff)
+```
+
+## Create Dataset with Difference Between Growth and Decay Dwell Times as its own Variable
+
+```{r}
+fractal_data_wide <- fractal_data %>% 
+  pivot_wider(names_from = direction,
+              values_from = dwell_time) %>% 
+  select(-Random) %>% 
+  mutate(Growth = unlist(Growth),
+         Decay = unlist(Decay),
+         diff_dwell_time = Growth - Decay)
+
+fractal_data_wide %>%   
+  group_by(participant) %>% 
+  summarise(mean_diff_dwell_time = mean(diff_dwell_time)) %>% 
+  knitr::kable(col.names = c("Participant", "Mean Difference in Dwell Times between Growth and Decay"))
+```
+
+## Descriptive Stats by Participant
+
+```{r}
+fractal_data %>% 
+  group_by(participant) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3)) %>% 
+  knitr::kable(col.names = c("Participant", "Dwell Time Mean", "Dwell Time SD"))
+```
+
+## Descriptive Statistics by Direction
+
+```{r}
+fractal_data %>% 
+  group_by(direction) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3)) %>% 
+  knitr::kable(col.names = c("Direction", "Dwell Time Mean", "Dwell Time SD"))
+```
+
+## Descriptive Statistics by Fractal
+
+```{r}
+fractal_data %>% 
+  group_by(disp_image) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3)) %>% 
+  arrange(mean_dwell_time) %>% 
+  knitr::kable(col.names = c("Fractal", "Dwell Time Mean", "Dwell Time SD"))
+```
+
+## Descriptive Statistics by Participant and Direction
+
+```{r}
+fractal_data %>% 
+  group_by(participant, direction) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3)) %>% 
+  knitr::kable(col.names = c("Participant", "Direction", "Dwell Time Mean", "Dwell Time SD"))
+```
+
+## A Couple of Plots
+
+```{r}
+new_data_for_now <- fractal_data %>% 
+  group_by(participant, direction) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3))
+
+new_data_for_later <- fractal_data %>% 
+  group_by(direction) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3))
+
+fractal_data %>% 
+  ggplot(aes(x = direction, y = dwell_time, fill = direction)) +
+  geom_col(data = new_data_for_later, aes(y = mean_dwell_time)) +
+  labs(x = "Direction", y = "Dwell Time (s)", title = "Dwell Times by Condition") +
+  theme(legend.position = "none") +
+  scale_fill_viridis_d()
+
+fractal_data %>% 
+  ggplot(aes(x = direction, y = dwell_time, fill = direction)) +
+  geom_col(data = new_data_for_now, aes(y = mean_dwell_time)) +
+  facet_wrap(~participant, scales = "free") +
+  labs(x = "Direction", y = "Dwell Time (s)", title = "Dwell Times by Condition for Each Participant", subtitle = "(y axis scale varies by participant)") +
+  theme(legend.position = "none") +
+  scale_fill_viridis_d() +
+  theme(axis.text.x = element_text(size = 7))
+```
+
+## Building a Model (and a Plot for that Model)
+
+```{r}
+model1 <- lm(data = fractal_data, dwell_time ~ direction)
+
+summary(model1)
+
+car::Anova(model1)
+
+sjPlot::plot_model(model1, type = "pred", terms = c("direction"))
+```
+
+## More Models and Plots
+
+```{r}
+seq_fractal_data <- fractal_data %>% 
+  filter(direction != "Random") %>% 
+  mutate(sequence_position = factor(sequence_position),
+         fractal_type = factor(fractal_type))
+
+new_data_forever <- seq_fractal_data %>% 
+  group_by(sequence_position, fractal_type) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3))
+
+seq_fractal_data %>% # change points to numbers for easy sequence position identification
+  ggplot(aes(x = fractal_type, y = dwell_time, color = sequence_position)) +
+  geom_point(data = new_data_forever, aes(y = mean_dwell_time)) +
+  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
+
+model2 <- lm(data = seq_fractal_data, dwell_time ~ sequence_position * fractal_type)
+
+car::Anova(model2)
+
+seq_fractal_data %>% 
+  ggplot(aes(x = sequence_position, y = dwell_time)) +
+  facet_wrap(~fractal_type) +
+  geom_point(data = new_data_forever, aes(y = mean_dwell_time)) +
+  scale_y_continuous(limits = c(0, 1.2)) +
+  labs(y = "Dwell Time (s)", x = "Sequence Position")
+```
+
+## Dwell Time over Time (yeah, that's right)
+
+### These plots show how dwell time decreased over time as participants became bored, fatigued, etc.
+The order of the fractals was counterbalanced such that the A group and the B group saw the fractal types in the reverse order.
+
+```{r}
+raw_A_long %>% 
+  ggplot(aes(x = number, y = dwell_time, color = participant)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = F)
+
+raw_B_long %>% 
+  ggplot(aes(x = number, y = dwell_time, color = participant)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = F)
+
+raw_A_long %>% 
+  ggplot(aes(x = number, y = dwell_time, color = participant)) +
+  geom_line()
+
+raw_B_long %>% 
+  ggplot(aes(x = number, y = dwell_time, color = participant)) +
+  geom_line()
+
+raw_A_long %>% 
+  ggplot(aes(x = number, y = dwell_time)) +
+  facet_wrap("participant") +
+  geom_line() +
+  geom_smooth(method = "lm", se = F)
+
+raw_B_long %>% 
+  ggplot(aes(x = number, y = dwell_time)) +
+  facet_wrap("participant") +
+  geom_line() +
+  geom_smooth(method = "lm", se = F)
+```

### 2020-11-18 chaloupka_sameshima_wallner_final_project.Rmd
Peer review
Added an image folder, and an inline image, plus a few ponderings.

@@
 ---
+<!-- Using the papaja format would be good here, as it would provide a place for an abstract that would help the casual observer understand your project. -->
+
+## "Our primary research question is whether observer dwell times systematically differ between growth and decay sequences when given the image of a fractal in growth or decay." 
+![here is a serious sierpinski sequence](images/fractal_sequences.png)
 

### 2020-11-18 chaloupka_sameshima_wallner_final_project.Rmd

@@
 ```
-
+<!-- I wonder how hard it would be to make it so each data set had 8 participants. I tried briefly and it didn't like that, as the raw data has 6 and 10 columns, not 8 and 8. -->
 ## Create New Dataset Excluding Outliers
@@
   scale_y_continuous(limits = c(0, 1.2)) +
-  labs(y = "Dwell Time (s)", x = "Sequence Position")
+  labs(y = "Dwell Time(s)", x = "Sequence Position")
 ```
+<!-- eliminated extra space in Dwell Time(s) -->
 

### 2020-11-18 chaloupka_sameshima_wallner_final_project.Rmd
Peer review!
GREAT JOB! - Maggie

--- 2020-11-16 chaloupka_sameshima_wallner_final_project.Rmd
@@
   filter(dwell_time < cutoff)
+
 ```
@@
 ## Building a Model (and a Plot for that Model)
+<!-- If you want to build a model, you might want to check the assumptions of the residuals too. -->
+<!-- -From Maggie :) -->
+```{r}
+library(lm.beta)
+library(MASS)
+library(psych)
+library(lmtest)
+
+#confidence intervals:
+confint(model1)
+# Create a new column and append the Unstandardized model predicted values
+
+data$pred   <- predict(model1)
+
+# Create a new column and append the Studentized Residuals
+
+data$zresid <- studres(model1)
+
+# Compute the absolute value of studentized residuals
+
+data$abs.zresid <- abs(data$zresid)
+
+# Create a new column and append the Studentized Deleted Residuals
+
+data$stdresid <- rstudent(model1)
+
+# Create a new column and append the Hat Values
+
+data$hat <- hatvalues(model1)
+
+```
 
@@
   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) 
+  # + labs(color = "Sequence Position")
+#It may be helpful to have clear labels with spaces in a final manuscript (rather than underscores). I added a legend label above.
 

### 2020-11-22 chaloupka_sameshima_wallner_final_project.Rmd

--- 2020-11-18 chaloupka_sameshima_wallner_final_project.Rmd
@@
 ---
-<!-- Using the papaja format would be good here, as it would provide a place for an abstract that would help the casual observer understand your project. -->
-
-## "Our primary research question is whether observer dwell times systematically differ between growth and decay sequences when given the image of a fractal in growth or decay." 
-![here is a serious sierpinski sequence](images/fractal_sequences.png)
 
@@
     grepl("B12800.png", disp_image, fixed = T) ~ 9
-  ))
+  )) #very organized!
+curious if you can make this chunk shorter (like coding all with "3.png" as 4), but I am not sure if you have a pattern to follow like that, based on what I see here.
+Either way, this works.
 
@@
   knitr::kable(col.names = c("Participant", "Dwell Time Mean", "Dwell Time SD"))
+
+# would be curious to see this visually represented, like a boxplot per participant to compare means, sds, and distributions
 ```
@@
   knitr::kable(col.names = c("Fractal", "Dwell Time Mean", "Dwell Time SD"))
+
+# is there a way to make the name of the fractal more meaningful here? I am of course no content expert, but I was curious if the Images/ prefix and .png suffix are needed
 ```
@@
   facet_wrap(~participant, scales = "free") +
-  labs(x = "Direction", y = "Dwell Time (s)", title = "Dwell Times by Condition for Each Participant", subtitle = "(y axis scale varies by participant)") +
+  labs(x = "Direction", y = "Dwell Time (s)", title = "Dwell Times by Condition for Each Participant", subtitle = "y axis scale varies by participant") +
   theme(legend.position = "none") +
@@
   theme(axis.text.x = element_text(size = 7))
+
+# this faceted visual is very cool!!!!!
+# I'm curious how the dwell time compares across participants, so I just explored that below
+
+fractal_data %>% 
+  ggplot(aes(x = participant, y = dwell_time, fill = participant)) +
+  geom_col(data = new_data_for_now, aes(y = mean_dwell_time)) +
+  facet_wrap(~direction, scale = "free") +
+  labs(x = "Participant", y = "Dwell Time (s)", title = "Dwell Times by Condition for Each Participant", subtitle = "y axis scale varies by participant") +
+  theme(legend.position = "none") +
+  scale_fill_viridis_d() +
+  theme(axis.text.x = element_text(size = 7)) +
+  coord_flip()
+
 ```
@@
   geom_smooth(method = "lm", se = F)
+
+# would be interested to see how you interpret these graphs in your paper! overall, really cool work
 ```

### 2020-11-25 chaloupka_sameshima_wallner_final_project.Rmd
add images and gif
added fractal images and gif files to repo and RWD

--- 2020-11-18 chaloupka_sameshima_wallner_final_project.Rmd
@@
 theme_set(theme_minimal())
+```
+
+## Fractal Iteration GIF
+
+```{r}
+
+library(magick)
+
+Tree_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4nts3v.gif")
+
+Fractal_Curve_C <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntsf7.gif")
+
+Sierpinski_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntsnw.gif")
+
+Hilbert <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntswb.gif")
+
+Pythagoras_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntt1q.gif")
+
+Tree_A
+Fractal_Curve_C
+Sierpinski_A
+Hilbert
+Pythagoras_A
+
 ```
@@
   filter(dwell_time < cutoff)
-
 ```
@@
 ## Building a Model (and a Plot for that Model)
-<!-- If you want to build a model, you might want to check the assumptions of the residuals too. -->
-<!-- -From Maggie :) -->
-```{r}
-library(lm.beta)
-library(MASS)
-library(psych)
-library(lmtest)
-
-#confidence intervals:
-confint(model1)
-# Create a new column and append the Unstandardized model predicted values
-
-data$pred   <- predict(model1)
-
-# Create a new column and append the Studentized Residuals
-
-data$zresid <- studres(model1)
-
-# Compute the absolute value of studentized residuals
-
-data$abs.zresid <- abs(data$zresid)
-
-# Create a new column and append the Studentized Deleted Residuals
-
-data$stdresid <- rstudent(model1)
-
-# Create a new column and append the Hat Values
-
-data$hat <- hatvalues(model1)
-
-```
 
@@
   theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
-  # + labs(color = "Sequence Position")
-#It may be helpful to have clear labels with spaces in a final manuscript (rather than underscores). I added a legend label above.
 

### 2020-11-25 chaloupka_sameshima_wallner_final_project.Rmd
Add Presentation
added presentation .Rmd and updated writeup .Rmd with new/updated figures and such

@@
 theme_set(theme_minimal())
-```
-
-## Fractal Iteration GIF
-
-```{r}
-
-library(magick)
-
-Tree_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4nts3v.gif")
-
-Fractal_Curve_C <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntsf7.gif")
-
-Sierpinski_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntsnw.gif")
-
-Hilbert <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntswb.gif")
-
-Pythagoras_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntt1q.gif")
-
-Tree_A
-Fractal_Curve_C
-Sierpinski_A
-Hilbert
-Pythagoras_A
-
 ```
@@
 
-seq_fractal_data %>% 
-  ggplot(aes(x = sequence_position, y = dwell_time)) +
+temp <- seq_fractal_data %>% 
+  mutate(seq_pos2 = case_when(
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 1 ~ 18,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 2 ~ 17,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 3 ~ 16,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 4 ~ 15,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 5 ~ 14,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 6 ~ 13,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 7 ~ 12,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 8 ~ 11,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 9 ~ 10,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 1 ~ 1,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 2 ~ 2,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 3 ~ 3,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 4 ~ 4,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 5 ~ 5,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 6 ~ 6,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 7 ~ 7,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 8 ~ 8,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 9 ~ 9,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 1 ~ 12,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 2 ~ 11,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 3 ~ 10,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 4 ~ 9,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 5 ~ 8,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 6 ~ 7,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 1 ~ 1,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 2 ~ 2,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 3 ~ 3,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 4 ~ 4,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 5 ~ 5,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 6 ~ 6,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 1 ~ 16,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 2 ~ 15,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 3 ~ 14,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 4 ~ 13,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 5 ~ 12,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 6 ~ 11,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 7 ~ 10,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 8 ~ 9,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 1 ~ 1,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 2 ~ 2,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 3 ~ 3,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 4 ~ 4,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 5 ~ 5,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 6 ~ 6,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 7 ~ 7,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 8 ~ 8,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 1 ~ 10,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 2 ~ 9,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 3 ~ 8,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 4 ~ 7,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 5 ~ 6,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 1 ~ 1,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 2 ~ 2,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 3 ~ 3,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 4 ~ 4,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 5 ~ 5,
+    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 1 ~ 8,
+    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 2 ~ 7,
+    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 3 ~ 6,
+    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 4 ~ 5,
+    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 1 ~ 1,
+    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 2 ~ 2,
+    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 3 ~ 3,
+    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 4 ~ 4))
+
+new_data_never <- temp %>% 
+  group_by(seq_pos2, fractal_type) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3))
+
+temp %>% 
+  ggplot(aes(x = seq_pos2, y = dwell_time, color = fractal_type)) +
   facet_wrap(~fractal_type) +
-  geom_point(data = new_data_forever, aes(y = mean_dwell_time)) +
-  scale_y_continuous(limits = c(0, 1.2)) +
-  labs(y = "Dwell Time (s)", x = "Sequence Position")
+  geom_point(data = new_data_never, aes(y = mean_dwell_time)) +
+  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
+  scale_y_continuous(limits = c(0, 1.4)) +
+  geom_line(data = new_data_never, aes(y = mean_dwell_time)) +
+  theme(legend.position = "none") +
+  scale_color_viridis_d()
+
+unique(seq_fractal_data$fractal_type)
 ```
@@
   ggplot(aes(x = number, y = dwell_time, color = participant)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = F)
+  geom_point(alpha = .6) +
+  geom_smooth(method = "lm", se = F) +
+  labs(title = "Unfolding Dwell Times Over Duration of Task", subtitle = "Group 1: Fractal Curves -> Tree Fractal", x = "Image Number (for entire task)", y = "Dwell Time (s)", color = "Participant")
 
@@
   ggplot(aes(x = number, y = dwell_time, color = participant)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = F)
+  geom_point(alpha = .6) +
+  geom_smooth(method = "lm", se = F) +
+  labs(title = "Unfolding Dwell Times Over Duration of Task", subtitle = "Group 2: Tree Fractal -> Fractal Curves", x = "Image Number (for entire task)", y = "Dwell Time (s)", color = "Participant")
+```
 
+```{r}
 raw_A_long %>% 

### 2020-11-25 presentation.Rmd
Add Presentation
added presentation .Rmd and updated writeup .Rmd with new/updated figures and such

---
title: "Untitled"
author: "Scott Wallner, Tess Sameshima, & Ben Chaloupka"
date: "11/25/2020"
output:
  revealjs::revealjs_presentation:
    theme:  blood
    center: TRUE
    self_contained: FALSE
---

# This is our title

## Authors

Scott Wallner, Tess Sameshima, and Ben Chaloupka

# Ben Chaloupka

## Challenges faced along the way

this text will appear on the slide

## Victories and things to celebrate

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Fractal Dwell Time Schematic.jpg" height="360" width="480">

## Challenges you are still facing

## Substantive findings and interpretations

## Next R hurdle to tackle

# Tess Sameshima

## Challenges faced along the way

## Victories and things to celebrate

## Challenges you are still facing

## Substantive findings and interpretations

## Next R hurdle to tackle

# Scott Wallner

## Challenges faced along the way

## Victories and things to celebrate

## Challenges you are still facing

## Substantive findings and interpretations

## Next R hurdle to tackle

# Conclusions

## Thank you slide

### 2020-11-26 presentation.Rmd
changes to presentation
working on my sections of the presentation

@@
 ---
-title: "Untitled"
+title: "EDLD 651 Final Project Presentation"
 author: "Scott Wallner, Tess Sameshima, & Ben Chaloupka"
@@
 
-# This is our title
+```{r include = FALSE}
+
+knitr::opts_chunk$set(echo = FALSE,
+                      message = FALSE,
+                      warning = FALSE)
+
+library(revealjs)
+```
+
+# Dwelling on Complexity with Dynamic Fractals
+*How much time will participants spend looking at dynamic fractals as they increase or decrease in complexity?*
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mandy4.png" height="360" width="480">
 
@@
 
-# Ben Chaloupka
+# Ben "Turtles all the way down," Chaloupka
 
@@
 
-## Substantive findings and interpretations
-
 ## Next R hurdle to tackle
 
-# Tess Sameshima
+# Tess "Best hair superlative champion," Sameshima
 
@@
 
-## Substantive findings and interpretations
+## Next R hurdle to tackle
+
+# Scott "Dad jokes for days," Wallner
+
+## Challenges faced along the way
+- data wrangling
+  - cleaning name 
+  - large data sets
+  - many separate data files for participants and conditions
+  - needed to use both long and wide formats
+
+## Victories and things to celebrate
+- making GIFs
+- super neat plots
+- research question was answered
+- hypothesis was correct
+
+## Challenges you are still facing
+- make some plots prettier
 
 ## Next R hurdle to tackle
+- remove outliers and re-run analysis
+- power analysis
+- adapt and develop the study
+- run an online study
+- replicate with cellular automata and 3D dynamic fractals
 
-# Scott Wallner
+# Project Background and Introduction
 
-## Challenges faced along the way
+## What are fractals?
 
-## Victories and things to celebrate
+- Invented by Benoit Mandelbrot in 1980
+  *"Clouds are not spheres. Mountains are not triangles."*
+- Measure of "roughness" called dimension
+- Self similarity and scale invariance
+- Mathematically or algorithmically generated
+- Pervasive in nature
 
-## Challenges you are still facing
+## Statistical Fractal Images
 
-## Substantive findings and interpretations
+<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Images Example Array.png" height="600" width="800">
 
-## Next R hurdle to tackle
+## The Dwell Time Paradigm
+
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="600" width="800">
+
+## Growth, Decay and Random Presentations
+
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Presentation Sequences.png" height="600" width="800">
+
+##
+
+<div class="col">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntsf7.gif" height="300" width="400">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntt1q.gif" height="300" width="400">
+</div>
+
+<div class="col">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntsnw.gif" height="300" width="400">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4nts3v.gif" height="300" width="400">
+</div>
+
+# Substantive findings and interpretations
+
+## Ben
+
+## Tess
+
+## Scott
+
+<!-- <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/00scott.png" height="360" width="480"> -->
+
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/00scott.png" height="360" width="480">
 

### 2020-11-26 presentation.Rmd
changes to pres
continued working on my sections

@@
 - remove outliers and re-run analysis
-- power analysis
+- run a power analysis
 - adapt and develop the study
@@
 
+:::: {style="display: flex;"}
+
+:::{}
 - Invented by Benoit Mandelbrot in 1980
-  *"Clouds are not spheres. Mountains are not triangles."*
+- *"Clouds are not spheres. Mountains are not triangles."*
 - Measure of "roughness" called dimension
@@
 - Mathematically or algorithmically generated
-- Pervasive in nature
+:::
+
+:::{}
+<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/cloud5.png" height="300" width="400">
+:::
+
+::::
+
+## Where are fractals?...Everywhere!
+Fractals are pervasive in natural processes.
+
+:::: {style="display: flex;"}
+
+::: {}
+<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mountain2.png" height="200" width="300">
+<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/purple.png" height="200" width="300">
+:::
+
+::: {}
+<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/veins2.png" height="200" width="300">
+<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/tree2.png" height="200" width="300">
+:::
+
+::: {}
+<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/river3.png" height="200" width="300">
+<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mud.png" height="200" width="300">
+:::
+
+::::
 
@@
 
-## Ben
+## 
+<!-- Ben -->
 
-## Tess
+## 
+<!-- Tess -->
 
-## Scott
+## 
+<!-- Scott -->
+
+###
+<small> Dwell times ***increase*** as complexity ***increases*** during the ***growth*** phase.
+</small>
+
+<small>Dwell times ***decrease*** as complexity ***decreases*** during the ***decay*** phase.
+</small>
 
@@
 
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/00scott.png" height="360" width="480">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/00scott.png" height="480" width="640">
 

### 2020-11-27 presentation.Rmd
update presentation

@@
 # Dwelling on Complexity with Dynamic Fractals
+
 *How much time will participants spend looking at dynamic fractals as they increase or decrease in complexity?*
+
 <img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mandy4.png" height="360" width="480">
@@
 - hypothesis was correct
+- using R to make this presentation
 

### 2020-11-27 chaloupka_sameshima_wallner_final_project.Rmd
add plots
ran new analysis of mean DT by seqpos2

@@
 
+temp %>% 
+  ggplot(aes(x = seq_pos2, y = dwell_time, color = fractal_type)) +
+  geom_point(data = new_data_never, aes(y = mean_dwell_time)) +
+  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
+  scale_y_continuous(limits = c(0, 1.4)) +
+  geom_line(data = new_data_never, aes(y = mean_dwell_time)) +
+  theme(legend.position = "none") +
+  scale_color_viridis_d()
+
+temp2 <- temp %>% 
+  group_by(seq_pos2) %>% 
+  summarise(mean_dt = mean(dwell_time)) %>% 
+  mutate(mean_dt = mean_dt)
+
+temp2 %>% 
+  ggplot(aes(x = seq_pos2, y = mean_dt)) +
+  geom_point(data = temp2, aes(y = mean_dt)) +
+  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
+  scale_y_continuous(limits = c(0, 1.4)) +
+  theme(legend.position = "none") +
+  scale_color_viridis_d()
+
 unique(seq_fractal_data$fractal_type)

### 2020-11-28 chaloupka_sameshima_wallner_final_project.Rmd
work with new plots in rmd

--- 2020-11-25 chaloupka_sameshima_wallner_final_project.Rmd
@@
 
+# dwell times by sequence position and fractal type
+temp %>% 
+  ggplot(aes(x = seq_pos2, y = dwell_time, color = fractal_type)) +
+  geom_point(data = new_data_never, aes(y = mean_dwell_time)) +
+  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
+  scale_y_continuous(limits = c(0, 1.4)) +
+  geom_line(data = new_data_never, aes(y = mean_dwell_time)) +
+  theme(legend.position = "none") +
+  scale_color_viridis_d()
+
+temp2 <- temp %>% 
+  group_by(seq_pos2) %>% 
+  summarise(mean_dt = mean(dwell_time)) %>% 
+  mutate(mean_dt = mean_dt)
+
+# mean dwell times by sequence position
+
+temp2 %>% 
+  ggplot(aes(x = seq_pos2, y = mean_dt)) +
+  geom_point(data = temp2, aes(y = mean_dt)) +
+  labs(y = "Mean Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "Means across all fractal types") +
+  scale_y_continuous(limits = c(0, 1.4)) +
+  theme(legend.position = "none") +
+  scale_color_viridis_d()
+
 unique(seq_fractal_data$fractal_type)

### 2020-11-28 presentation.Rmd
update presentation

@@
 - run a power analysis
+- work with the "random" data
 - adapt and develop the study

### 2020-11-30 presentation.Rmd
update with Tess's text and figure

@@
 
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mandy4.png" height="360" width="480">
-
-## Authors
-
-Scott Wallner, Tess Sameshima, and Ben Chaloupka
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mandy4.png" height="360" width="480">
 
@@
 
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Fractal Dwell Time Schematic.jpg" height="360" width="480">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="360" width="480">
 
@@
 ## Challenges faced along the way
+- Technological issues 
+  - Version control
+  - Multi OS nomenclature
+  - Error bars
+
+ ![Alt Text](https://media.giphy.com/media/wvQIqJyNBOCjK/giphy.gif)
 
 ## Victories and things to celebrate
+- Technological work arounds
+  - More familiar with path settings
+  - General code interpretation and debugging improvements
 
 ## Challenges you are still facing
+- Fluid coding
+- More error feed back comprehension
 
 ## Next R hurdle to tackle
+- Using R to analyze data collected in MATLAB
+- Using R for my master's project
 
@@
 :::{}
-<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/cloud5.png" height="300" width="400">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/cloud5.png" height="225" width="300">
 :::
@@
 ::: {}
-<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mountain2.png" height="200" width="300">
-<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/purple.png" height="200" width="300">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mountain2.png" height="200" width="300">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/purple.png" height="200" width="300">
 :::
@@
 ::: {}
-<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/veins2.png" height="200" width="300">
-<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/tree2.png" height="200" width="300">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/veins2.png" height="200" width="300">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/tree2.png" height="200" width="300">
 :::
@@
 ::: {}
-<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/river3.png" height="200" width="300">
-<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mud.png" height="200" width="300">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/river3.png" height="200" width="300">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mud.png" height="200" width="300">
 :::
@@
 
-<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Images Example Array.png" height="600" width="800">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Images Example Array.png" height="600" width="800">
 
@@
 
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="600" width="800">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="600" width="800">
 
@@
 
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Presentation Sequences.png" height="600" width="800">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Presentation Sequences.png" height="600" width="800">
 
@@
 <div class="col">
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntsf7.gif" height="300" width="400">
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntt1q.gif" height="300" width="400">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntsf7.gif" height="300" width="400">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntt1q.gif" height="300" width="400">
 </div>
@@
 <div class="col">
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntsnw.gif" height="300" width="400">
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4nts3v.gif" height="300" width="400">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntsnw.gif" height="300" width="400">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4nts3v.gif" height="300" width="400">
 </div>
@@
 <!-- Tess -->
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/ovr_dwell_time2.png" height = "300" width = "400">
 
@@
 
-<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/00scott.png" height="480" width="640">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/00scott.png" height="480" width="640">
 

### 2020-11-30 chaloupka_sameshima_wallner_final_project.Rmd
Updated with Ben's text

@@
   summarise(mean_dwell_time = round(mean(dwell_time), 3),
-            sd_dwell_time = round(sd(dwell_time), 3))
+            sd_dwell_time = round(sd(dwell_time), 3),
+            mean_se_dwell_time = round(plotrix::std.error(dwell_time), 3))
 
-fractal_data %>% 
-  ggplot(aes(x = direction, y = dwell_time, fill = direction)) +
-  geom_col(data = new_data_for_later, aes(y = mean_dwell_time)) +
+ymin = new_data_for_later$mean_dwell_time - new_data_for_later$mean_se_dwell_time
+ymax =new_data_for_later$mean_dwell_time + new_data_for_later$mean_se_dwell_time
+
+new_data_for_later %>% 
+  ggplot(aes(x = direction, y = mean_dwell_time, fill = direction)) +
+  geom_col() +
   labs(x = "Direction", y = "Dwell Time (s)", title = "Dwell Times by Condition") +
   theme(legend.position = "none") +
+  geom_errorbar(aes(ymin = ymin, ymax = ymax, width = .5)) +
   scale_fill_viridis_d()

### 2020-11-30 presentation.Rmd
Updated with Ben's text

@@
 
-# Dwelling on Complexity with Dynamic Fractals
+## Dwelling on Complexity with Dynamic Fractals
 
-*How much time will participants spend looking at dynamic fractals as they increase or decrease in complexity?*
+How much time will participants spend looking at dynamic fractals as they increase or decrease in complexity?
 
@@
 ## Challenges faced along the way
-
-this text will appear on the slide
+- Working with Git
+  - Figuring out best practices for collaboration
+- Working with GGPlot
+  - Getting figures to display the right data
+- Not getting distracted by all the pretty fractals
 
 ## Victories and things to celebrate
-
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="360" width="480">
+- We made our presentation in R
+- We made a lot of sweet plots
+- We worked well as a team
+- I came away from this project knowing more about R than I did before
 
 ## Challenges you are still facing
+- Touching up some plots
+- Getting more efficient using Git
 
 ## Next R hurdle to tackle
+- Use functions we learned in class on my own data
+- Get better at commenting my code
 
@@
 <!-- Ben -->
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/group1.png" height = "600" width = "800">
+
+##
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/group2.png" height = "600" width = "800">
 
@@
 <!-- Tess -->
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/ovr_dwell_time2.png" height = "300" width = "400">
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/ovr_dwell_time2.png" height = "600" width = "800">
 

### 2020-11-30 presentation.Rmd
a few last minute changes
added extra figure and final gif

@@
 
-###
 <small> Dwell times ***increase*** as complexity ***increases*** during the ***growth*** phase.
@@
 
-<!-- <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/00scott.png" height="360" width="480"> -->
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/0007.png" height="480" width="640">
+
+##
+<small> Dwell times ***increase*** as complexity ***increases*** during the ***growth*** phase.
+</small>
+
+<small>Dwell times ***decrease*** as complexity ***decreases*** during the ***decay*** phase.
+</small>
 
@@
 
-## Thank you slide
+##
+We all admit, that we had a blast with this project.
+
+<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/83QZ.gif" height="400" width="800">

### 2020-11-30 presentation.Rmd
last minute tweak

@@
 - Invented by Benoit Mandelbrot in 1980
-- *"Clouds are not spheres. Mountains are not triangles."*
+- *"Clouds are not spheres. Mountains are not cones."*
 - Measure of "roughness" called dimension

### 2020-11-30 chaloupka_sameshima_wallner_final_project.Rmd
ggridges
trying to use ggridges to show the by sequence position plot spread across different ridges. help if you can fix the error.

@@
 
+# trying to use ggridges
+
+library(ggridges)
+
+new_data_never %>% 
+  ggplot(aes(x = seq_pos2, y = mean_dwell_time, color = fractal_type)) +
+  geom_density_ridges() +
+  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
+  scale_y_continuous(limits = c(0, 1.4)) +
+  theme(legend.position = "none") +
+  scale_color_viridis_d()
+
 unique(seq_fractal_data$fractal_type)

### 2020-11-30 presentation.Rmd
some more edits

@@
 
-## Challenges faced along the way
+## Challenges along the way
 - Working with Git
@@
 
-## Victories and things to celebrate
+## Victories and celebrations
 - We made our presentation in R
@@
 
-## Challenges you are still facing
+## Remaining Challenges
 - Touching up some plots
@@
 
-## Challenges faced along the way
+## Challenges along the way
 - Technological issues 
@@
 
-## Victories and things to celebrate
+## Victories and and celebrations
 - Technological work arounds
@@
 
-## Challenges you are still facing
+## Remaining Challenges
 - Fluid coding
@@
 
-## Challenges faced along the way
+## Challenges along the way
+
+:::: {style="display: flex;"}
+
+:::{}
 - data wrangling
-  - cleaning name 
-  - large data sets
-  - many separate data files for participants and conditions
-  - needed to use both long and wide formats
+  - many separate data files
+  - needed long and wide
+  - cleaning names
+:::
 
-## Victories and things to celebrate
+:::{}
+ <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/cleaning.png" height="250" width="400">
+:::
+
+::::
+
+## Victories and celebrations
 - making GIFs
@@
 
-## Challenges you are still facing
+## Remaining Challenges
 - make some plots prettier

### 2020-12-02 presentation.Rmd
last minute update

@@
 - super neat plots
+- proof of concept and task
 - research question was answered
@@
 - using R to make this presentation
-
-## Remaining Challenges
-- make some plots prettier
 
@@
 - work with the "random" data
+- make some plots prettier
+
+## Remaining Challenges
 - adapt and develop the study
 - run an online study
-- replicate with cellular automata and 3D dynamic fractals
+- 3D dynamic fractals
+- replicate with cellular automata
 

### 2020-12-04 presentation.Rmd
added paper draft and ref doc
added a word doc of the final paper draft and added a reference list doc

@@
 
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mandy4.png" height="360" width="480">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mandy4.png" height="360" width="480">
 
@@
 :::{}
- <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/cleaning.png" height="250" width="400">
+ <img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/cleaning.png" height="250" width="400">
 :::
@@
 :::{}
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/cloud5.png" height="225" width="300">
+<!-- <img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/cloud5.png" height="225" width="300"> -->
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/cloud5.png" height="225" width="300">
+
 :::
@@
 ::: {}
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mountain2.png" height="200" width="300">
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/purple.png" height="200" width="300">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mountain2.png" height="200" width="300">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/purple.png" height="200" width="300">
 :::
@@
 ::: {}
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/veins2.png" height="200" width="300">
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/tree2.png" height="200" width="300">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/veins2.png" height="200" width="300">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/tree2.png" height="200" width="300">
 :::
@@
 ::: {}
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/river3.png" height="200" width="300">
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/Natural Fractals/mud.png" height="200" width="300">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/river3.png" height="200" width="300">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mud.png" height="200" width="300">
 :::
@@
 
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Images Example Array.png" height="600" width="800">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Images Example Array.png" height="600" width="800">
 
@@
 
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="600" width="800">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="600" width="800">
 
@@
 
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Presentation Sequences.png" height="600" width="800">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/Fractal Presentation Sequences.png" height="600" width="800">
 
@@
 <div class="col">
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntsf7.gif" height="300" width="400">
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntt1q.gif" height="300" width="400">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntsf7.gif" height="300" width="400">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntt1q.gif" height="300" width="400">
 </div>
@@
 <div class="col">
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4ntsnw.gif" height="300" width="400">
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/4nts3v.gif" height="300" width="400">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4ntsnw.gif" height="300" width="400">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/4nts3v.gif" height="300" width="400">
 </div>
@@
 <!-- Ben -->
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/group1.png" height = "600" width = "800">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/group1.png" height = "600" width = "800">
 
 ##
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/group2.png" height = "600" width = "800">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/group2.png" height = "600" width = "800">
 
@@
 <!-- Tess -->
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/ovr_dwell_time2.png" height = "600" width = "800">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/ovr_dwell_time2.png" height = "600" width = "800">
 
@@
 
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/0007.png" height="480" width="640">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/0007.png" height="480" width="640">
 
@@
 
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/00scott.png" height="480" width="640">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/00scott.png" height="480" width="640">
 
@@
 
-<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/83QZ.gif" height="400" width="800">
+<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/83QZ.gif" height="400" width="800">

### 2020-12-07 paper/paper_papaja.rmd
Paper folder & contents

---
title             : "Fractals are Cool"
shorttitle        : "Everything is Fractal"
documentclass     : "apa6"
classoption       : "jou"
output            : papaja::apa6_pdf
indent            : True

author: 
  - name          : "Ben Chaloupka"
    affiliation   : "1"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
      - Grand Master Coding Wizard
  - name          : "Tesufuai Sameshima"
    affiliation   : "1"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
       - Writing - Original Draft Preparation
       - Writing - Review & Editing
       - Token Black Man
  - name          : "Scott Wallner"
    affiliation   : "1"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
       - Conceptualization
       - Writing - Original Draft Preparation
       - Writing - Review & Editing
       - Resident Fractal Expert

affiliation:
  - id            : "1"
    institution   : "University of Oregon"

authornote: |
 Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |   
 Fractals can be described as geometric objects which contain self similarity and scale invariance. Fractal objects and fractal properties are pervasive in nature.  Many processes which involve replication or growth can be modeled with fractal mathematics. The formalized mathematics of fractals has been used as an analog for complexity, an important property related to human cognition. Studies have shown that human perception has evolved to process fractals fluently, as well as exhibit aesthetic preferences for fractals. The experience of fractals in a number of domains have proven to be therapeutically useful. Previous studies have used independent and static fractal images to investigate the relationship between, fractals, complexity and human perception. This study employs a Dwell Time Paradigm to present self paced slide shows of dynamic fractals in an unfolding process of iterative growth and decay. Results of measured looking or dwell times show that participants prefer viewing fractals as they grow through phases of increasing complexity compared to decay phases of decreasing complexity. Longer dwell times for higher complexity may indicate that human perception is captured by the surprising or novel nature of a fractal’s iterative growth process.

 This study is the first to use a novel presentation of dynamic fractal processes to explore fractal fluency and aesthetic preference. Results from 16 participants prove that dynamic fractals can be integrated into the well established dwell time paradigm. These findings can be used to develop new techniques for utilizing fractals as therapeutic tools.
  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

---

```{r setup, include = FALSE}
library(janitor)
library("papaja")
r_refs("r-references.bib")
# Sys.setenv(LANG = "en")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
  Fractal is a term originally derived to describe the “roughness,” (Mandelbrot) of objects, surfaces, or textures.  Fractal properties are pervasive throughout nature (Losa) and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.  These fractal properties are identified by their self-similarity and scale invariance. Self-similarity implies that a part of the structure maintains the same structure or pattern as the whole.  For example, if one were to zoom in on a small stretch of coastline, the jagged edges would look similar to the jaggedness of the coastline from a broader view.  Likewise, a small section of a fern is nearly identical to the branching shape of the entire fern.

```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
knitr::include_graphics(here::here("paper","paper_images","coast.jpg"))
knitr::include_graphics(here::here("paper","paper_images","fractalfern.png"))
knitr::include_graphics(here::here("paper","paper_images","spooky.png"))

```

  Scale-invariance is a related mathematical property which can be applied to objects or laws that do not change if scales of length, energy, or other variables, are multiplied by a common factor, and thus represent a universality. (wiki, scale invariance)  Expressed more intuitively, scale invariance implies that it does not matter at which scale one views and object or observes a process, because the object or process contains a commonality at all scales.

  It is interesting and important to note that the concept of fractal properties can be applied to objects like a snowflake, but also processes, like the crystallization of the snowflake. Crystals are created by repeating a simple process over and over in a feedback loop. A crystal starts with a tiny bit of structure, and that structure is repeated, growing on itself using the same pattern or rule for growth. This can be seen quite obviously in objects that are themselves fractals, such as the branching process of trees, but other natural processes follow the rules of fractals.  Hurricanes, avalanches, the diffusion of molecules in solution, the dissolving of porous rock, the electrical breakdown of dialectics, and in the growth of our lungs and brains.  Strikingly fractal properties can be found in statistical systems or distributions of word usage, foraging behaviors, rock size and in the frequency of scientific journal citations, and network outages of the internet. (Wiki, scale invariance) The underlying principle of fractals is that a simple process can through infinitely many iterations to become a very complex process. Many processes which involve bifurcation, splitting, replication and growth can be fractal mathematics and geometry. Fractal mathematics can model these complex systems by searching for the simple rules or laws that drive these processes. (http://pages.cs.wisc.edu/~ergreen/honors_thesis/fractal.html)

  In addition to inventing the term fractal, Mandelbrot developed a mathematics and geometry of fractals.  He devised a way to model and generate complex systems with a simple mathematical rule that could be run repeatedly or iterated on itself.  These iterative processes essentially use a rule to take an initial condition or state, change or modulate it, then put the resulting updated state back into the rule to generate another new state.  This can be repeated infinitely and often results in high complex objects or systems.  Fractal mathematics have continued to be developed and utilized in mathematics, physics, biology, chemistry, and engineering.  A recent application of fractal mathematics is utilized in computer generated images and models.  By starting with a simple algorithm, a mathematical equation or rule, graphic artists and programmers can create highly complex models of natural systems.

  By replicating the fractal processes in nature, computer programs can generate digital forests, mountain ranges, and coastlines.  These images can be found in movies and video games.  Similarly scientists and engineers can use fractal mathematics to generate models of complex systems that accurately represent patterns and processes in weather, cosmology, electronics, and statistics.

  Two premiere examples of these mathematical or statistical fractals can be seen in the Koch Curve and the Cantor Set.  In each case an image is created by starting with a single line segment and a rule for changing that line segment.  The cantor set can be visualized by displaying each cycle of the process of iteration together.  First a single line segment is displayed.  The Cantor Set rule divides the segment in three equal sections and removes the middle section, leaving two line segments each one third of the original length and separated by a space equal to one third of the original line segment.  The two separated line segments of the 2nd order iteration can be displayed beneath the original first order line segment.  The rule, dividing and removing a portion of the line segment is applied to the two new line segments.  Each of these line segments is divided into thirds and the middle third is removed. This results in four new smaller line segments spaced in a proportion equal to the previous two line segments.  These four line segments are again displayed under the two line segments.  This process can be repeated infinitely many times, dividing and removing segments at each iteration.  When displayed together, we are able to visualize the repeating pattern which relates to the simple unchanging rule.  This is an intuitive way to represent the properties of self-similarity, scale invariance, and iterative growth rules of fractals.  A similar example is the Koch Curve. Again we start with a single line segment, but define a new rule to change that line segment through each iteration.  Like the Cantor set, the line segment is divided into thirds, but instead of just removing the middle third which results in two new line segments, we bridge the middle third with two line segments that compose two sides of an isosceles triangle which spans the removed middle third of the original line.  This new segmented line of the 2nd order iteration appears as a line with a triangular bump or protrusion in the middle. The entire segment is composed of four connected line segments.  Again, by using the same algorithmic rule, divide a segment into thirds and span the removed middle third with an isosceles angle, and is applied to all four of the line segments created by the first iterative change.  Now each of these four line segments will include an angular bump or peak that spans their middle third.  These results in a set of 16 angular connected line segments.  Just as we did with the cantor set, and can do with all fractal growth iterations, we can continue applying the rule to the updated condition of the object.  This time, unlike the cantor set which displays all the iterations together, a single, new object is produced at each iteration.  We can visualize the growth process by displaying a few of these objects together.

```{r, fig.show = "hold", out.width =  "50%",fig.align = 'left'}
knitr::include_graphics(here::here("paper","paper_images","bars.png"))
knitr::include_graphics(here::here("paper","paper_images","star.jpg"))

```
  There are numerous examples of these types of geometric transformations which result in beautiful and striking constructions.  Some well known fractal geometries are known as, The Dragon Curve, Sierpinski Triangle, and Hilbert Curve.  These examples show the diversity of implementations of fractal properties in geometry.  The variety of initial conditions and algorithmic rules result in an astounding array of complex objects which have real world applications and instantiations.

```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
knitr::include_graphics(here::here("paper","paper_images","squigly.jpg"))
knitr::include_graphics(here::here("paper","paper_images","triangle.jpg"))
knitr::include_graphics(here::here("paper","paper_images","maze.jpg"))

```

  These examples provide intuition about fractal processes and properties for anyone who may not have any experience or deep knowledge of the underlying mathematics.  Even a surface level experience of the properties of fractals allow one to engage with challenging and complex mathematical ideas.  One such idea critical to fractal mathematics is dimensionality.  Many learn and understand the concept of dimension as it is traditionally explained in mathematics.  Most will understand that a line is considered as one dimensional and a plane as two dimensional.  One dimension, as in the line, allows for movement or positions in one degree of freedom, left and right or forward and backward.  Two dimensions allow for two degrees of freedom, left-right and forward-backward, or as we often see in the plane of a map, North, South, East, West.  It is also intuitive to relate to three dimensions, which describe objects and space which contains the two dimensions of a plane, but also a third degree of freedom as up and down.  Fractal mathematics introduces a concept of dimensionality that can exist between these integer values of 1, 2, or 3 dimensions.  A fractal like the Dragon Curve or Koch Curve can have a dimensionality between 1 and 2, such as 1.2, 1.5, or 1.74823. At first this concept feels counter intuitive.  The non-integer dimensionality occurs because the length of the curve between any two points on the Koch snowflake is effectively infinite. No small piece of it is line-like, but rather it is composed of an infinite number of segments joined at different angles. The fractal dimension of a curve can be explained intuitively by thinking of a fractal line as an object too detailed to be one-dimensional, but too simple to be two-dimensional. (https://en.wikipedia.org/wiki/Fractal_dimension) Another way to understand this is to consider the process by which the Koch Curve is constructed. As we continually modulate the object through iterations, we can add an infinite number of additional line segments which create innumerable jagged peaks.  The Koch Curve which began with a one dimensional line will continue to take up more and more space, eventually filling a two dimensional area.

```{r, out.height =  "30%",fig.align = 'left'}
knitr::include_graphics(here::here("paper","paper_images","morefractals.png"))
knitr::include_graphics(here::here("paper","paper_images","square.png"))

```

  In this way we can realize that the Koch Curve is neither one or two dimensional, it is somewhere in between.  Using fractal mathematics invented by Mandelbrot, we can calculate the dimensionality of any fractal including the Koch and Dragon Curves which have dimensionalities of 1.262 and 1.5236 respectively.  Similarly an object which begins as a two dimensional fractal, can be iterated to grow into the third dimension and have a calculated dimension between 2 and 3. Thus, dimensionality can be considered as the space filling capacity of a fractal.  But seen another way, fractal dimension is a ratio providing a statistical index of complexity comparing how detail in a pattern changes with the scale at which it is measured.  The connection between fractal dimension and complexity has been used to understand how biological systems including human perception contain or interact with complexity.

  Calculating fractal dimension is not restricted to geometric or statistical fractals as described above.  One can also calculate a D value, fractal dimension of natural objects like coastlines, the outlines of clouds, or the silhouettes of mountain ranges on the horizon. These ideas have been rigorously developed and investigated, exemplified in the University of Oregon’s Dr. Richard Taylor theory of Fractal Fluency.  Simply put, human vision has not only adapted to efficiently process and perceive the dimensionality of fractals in nature, but has evolved to prefer fractals of a certain dimensional range.

  To date there have been numerous research studies which explore the aesthetic preferences for fractals of different dimensions. Studies have included methods which present participants with a two alternative forced choice task of two fractals of differing dimension. Participants select the fractal image they prefer aesthetically and after viewing many pairs with differing dimensions, statistics are used to calculate the most preferred dimensionality range across participants. The overarching results of previous research have shown that humans, both adults and children prefer fractals within a range of dimensions that coincide with the fractal dimension that is found in natural objects and scenes, usually between 1.3 and 1.5.Remembering that fractal dimension is an analog for complexity, we can conclude that most humans prefer a moderate level of complexity compared to low or high complexity near the extremes. A secondary analysis of fractal fluency has shown that humans often also prefer fractal images to non-fractal images and that we prefer fractals which more closely resemble natural images to fractals which are geometrically exact. (Spehar, and Spies) Extensions on these research findings have led to the use of fractal images in therapeutic applications.  Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (Hagerhall), the reduction of stress using fractal art and architecture (Taylor) and even in the experience of hearing fractal melodies (Beauvois). There appears to be a clear link between, the fractal’s representation of complexity, the connection with natural objects and processes, and the human mind.

  Despite many studies which explore the link between fractals, complexity, and human perception and aesthetics, there are continued adaptations and developments to the body of work.  This study attempts to address a gap in the way these ideas are explored.  Here we employ a novel presentation of fractal images which has yet to be tested or analyzed.  Specifically most studies of fractal fluency and aesthetic preference have used static independent fractal images.  This means, participants are usually restricted to the selection of a single fractal image in a given trial, and an unrelated or random image in the next trial.

```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
knitr::include_graphics(here::here("paper","paper_images","blotches.png"))
knitr::include_graphics(here::here("paper","paper_images","moreblotches.png"))
knitr::include_graphics(here::here("paper","paper_images","deconstruction.png"))

```

  However our natural experience of the world is not so static, fragmented and simple, it is often dynamic, cohesive and alive. To create a more lifelike experience of fractals we present participants with the unfolding process of a fractal as it is iterated through its process of changing in complexity.  By allowing participants to view a series of fractal images which increase and decrease in complexity we can more effectively understand the human experience of fractals that more closely resemble the dynamic process of life.  The results of this study may provide new and exciting understandings related to fractal fluency and preference as well as inspire the development of therapeutic applications of fractals.

# Methods

  Participants viewed self paced slideshows of fractal images in sequences of iterative growth and decay phases as well as a random ordering.  The time spent viewing each image was measured as a Dwell Time, following the procedures of Baldwin et. al. 2019.  A set of images were generated for each of fourteen different fractal types iterated from 4 to 9 times.  Each participant viewed a sequential slideshow and a random slideshow.  Sequential slideshows presented each fractal type through phases of growth and decay from the least complex to most complex iterations and back down from most complex to least complex.  Random slideshows presented the entire set of fractal images in random order.  6 participants viewed Sequential Slideshow A, starting with Fractal Type 1 to Type 14, and Random Slideshow A starting with Fractal Image 1 to Image 174.  The remaining 10 participants viewed Sequential Slideshow B, starting with Fractal Type 14 to Type 1, and Random Slideshow B starting with Fractal Image 174 to Image 1.  This counterbalancing was included to address the findings of previous dwell time studies in which participants dwell times systematically decrease through the slideshow.  In this way, the same fractal types were not always seen at the beginning or end of the slideshow.  This balancing was then reversed in analysis so that each fractal type and the corresponding dwell times could be analyzed for the entire set of 16 participants together.  Fractal images were generated using Wolfram Mathematica and slideshows were programmed using PsychoPy 3.

```{r, fig.show = "hold", out.height =  "25%",fig.align = 'left'}
knitr::include_graphics(here::here("paper","paper_images","task_outline.jpg"))
knitr::include_graphics(here::here("paper","paper_images","fractal_direction.png"))
```

## Participants
The study recruited 16 healthy young adults aging from 16-35 through the UO sona system.

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

  In this study a dwell time paradigm which measures looking times of participants as they advance through a self paced slideshow, was used to measure the preferences for fractal images.  Slideshows were composed of a variety of different fractal types, each of which was presented in a sequential pattern of growth and decay of complexity.  Fractal images are abundant in nature, and fractal fluency theory (Taylor) has shown that humans have evolved perceptual preferences for fractal images. Previous studies have shown that both adults and children display patterns of aesthetic preference for a particular range of fractal dimension, a mathematical quantification analogous to complexity.  Work in these studies have found that preferences generally fall in a range of complexity which mimics the fractal dimension found in natural scenes.  Yet up to this point in time, these studies have utilized static and independent fractal images.  These studies also have generally employed an alternative forced choice paradigm to quantify participant’s preferences.  This study is novel in two ways.  First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology. (Baldwin, Kosie)  By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.  We suggest that a dwell time paradigm provides a more nuanced insight into aesthetic preference or interest in a given stimuli set.  Results from this study have verified that this is a reliable measure to capture looking patterns and preference for fractal images.  The second way in which this study provides new findings to the fractal fluency literature is by utilizing dynamic fractals.  As discussed earlier, fractals pervade nature, and human perception has been tuned to process and prefer images that reflect fractals in nature.  But often our experiences of natural scenes are not static or independent, like the stimuli which has been used in all previous studies.  To better replicate natural experiences this study utilized a slideshow of fractal images which iterate through phases of growing and decaying complexity.  We sought to investigate whether participants would prefer dynamic fractals as they grow or decay in complexity.  The results show that there is a significant difference in the preference for dynamic fractals in the growth and decay phases, and that participants prefer to view fractals as they grow in complexity.  This can be seen in the increasing dwell times during the growth phase, and decreasing dwell times during the decay phase.  What is striking is that this pattern was consistent across 14 different fractal types and across a variety of number of iterations.

  There are a few limitations to the present study which inspire the future directions of this line of research.  Only 16 subjects, all college aged students, participated in the study.  In the future we plan to acquire more participants and include a larger range of ages.  After analyzing the data, a typical trend in dwell time paradigms emerged.  This pattern is that dwell times generally decrease as the slideshow proceeds.  As one would imagine this could occur because participants lose interest or simply increase the rate at which they proceed.  In order to alleviate this trend, we plan to use a fewer total number of fractal types and include attention checks to break up the presentation of the slide show. Data from this study which indicate the most preferential fractal types can be used to select the highest quality fractal sequences for subsequent studies. This should induce a more consistent display of attention across the entire task.  In this initial study all subjects were presented with fractal sequences which began with a growth phase followed by a decay phase.  We are interested to include a second condition in which a proportion of the participants view fractal sequences which start with a decay phase followed by the growth phase.  In future analysis of this study, and subsequent studies we also plan to analyze the same fractal images presented in a randomized order.  An important goal of this research trajectory is to more closely replicate the experiences of fractals in nature.  For this reason we can design studies which use 3 dimensional fractal images and another biologically inspired stimuli type cellular automata.  Surveys including the Autism Spectrum Quotient, and perceptual tasks like visual search and card sorting can be correlated with dwell time data can be utilized to better understand individual preferences and perceptual proclivities for complexity.  
  This study was the first of its kind, utilizing dynamic fractals presented in a dwell time paradigm.  The results from this study have shown that these methods are reliable and informative in regards to research questions which explore and connect fractal fluency, human perception, preference for complexity.

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-12-07 paper/paper_papaja.tex
knitted .pdf

--- 2020-12-07 paper/paper_papaja.rmd
@@
----
-title             : "Fractals are Cool"
-shorttitle        : "Everything is Fractal"
-documentclass     : "apa6"
-classoption       : "jou"
-output            : papaja::apa6_pdf
-indent            : True
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[english,jou]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
+\else % if luatex or xelatex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage[]{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{
+            pdftitle={Fractals are Cool},
+            pdfkeywords={keywords},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
 
-author: 
-  - name          : "Ben Chaloupka"
-    affiliation   : "1"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-      - Grand Master Coding Wizard
-  - name          : "Tesufuai Sameshima"
-    affiliation   : "1"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-       - Writing - Original Draft Preparation
-       - Writing - Review & Editing
-       - Token Black Man
-  - name          : "Scott Wallner"
-    affiliation   : "1"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-       - Conceptualization
-       - Writing - Original Draft Preparation
-       - Writing - Review & Editing
-       - Resident Fractal Expert
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
-affiliation:
-  - id            : "1"
-    institution   : "University of Oregon"
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-authornote: |
- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+% Table formatting
+\usepackage{longtable}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
-  Enter author note here.
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
-abstract: |   
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\makeatother
+\shorttitle{Everything is Fractal}
+\author{Ben Chaloupka\textsuperscript{1}, Tesufuai Sameshima\textsuperscript{1}, \& Scott Wallner\textsuperscript{1}}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} University of Oregon}
+\keywords{keywords\newline\indent Word count: X}
+\usepackage{dblfloatfix}
+
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{csquotes}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
+
+\title{Fractals are Cool}
+
+\date{}
+
+\abstract{
 Fractals can be described as geometric objects which contain self similarity and scale invariance.
@@
 Results of measured looking or dwell times show that participants prefer viewing fractals as they grow through phases of increasing complexity compared to decay phases of decreasing complexity.
-Longer dwell times for higher complexity may indicate that human perception is captured by the surprising or novel nature of a fractal’s iterative growth process.
+Longer dwell times for higher complexity may indicate that human perception is captured by the surprising or novel nature of a fractal's iterative growth process.
 
@@
 These findings can be used to develop new techniques for utilizing fractals as therapeutic tools.
-  <!-- https://tinyurl.com/ybremelq -->
+}
 
-keywords          : "keywords"
-wordcount         : "X"
+\begin{document}
+\maketitle
 
-bibliography      : ["r-references.bib"]
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
----
-
-```{r setup, include = FALSE}
-library(janitor)
-library("papaja")
-r_refs("r-references.bib")
-# Sys.setenv(LANG = "en")
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
-
-# Introduction
-  Fractal is a term originally derived to describe the “roughness,” (Mandelbrot) of objects, surfaces, or textures.
+Fractal is a term originally derived to describe the \enquote{roughness,} (Mandelbrot) of objects, surfaces, or textures.
 Fractal properties are pervasive throughout nature (Losa) and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
@@
 
-```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","coast.jpg"))
-knitr::include_graphics(here::here("paper","paper_images","fractalfern.png"))
-knitr::include_graphics(here::here("paper","paper_images","spooky.png"))
+\begin{figure}
 
-```
+\includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/coast} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/fractalfern} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/spooky} \hfill{}
+
+\caption{ }\label{fig:unnamed-chunk-1}
+\end{figure}
 
@@
 Fractal mathematics can model these complex systems by searching for the simple rules or laws that drive these processes.
-(http://pages.cs.wisc.edu/~ergreen/honors_thesis/fractal.html)
+(\url{http://pages.cs.wisc.edu/~ergreen/honors_thesis/fractal.html})
 
@@
 
-```{r, fig.show = "hold", out.width =  "50%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","bars.png"))
-knitr::include_graphics(here::here("paper","paper_images","star.jpg"))
+\begin{figure}
 
-```
+\includegraphics[width=0.5\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/bars} \includegraphics[width=0.5\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/star} \hfill{}
+
+\caption{ }\label{fig:unnamed-chunk-2}
+\end{figure}
+
 There are numerous examples of these types of geometric transformations which result in beautiful and striking constructions.
@@
 
-```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","squigly.jpg"))
-knitr::include_graphics(here::here("paper","paper_images","triangle.jpg"))
-knitr::include_graphics(here::here("paper","paper_images","maze.jpg"))
+\begin{figure}
 
-```
+\includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/squigly} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/triangle} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/maze} \hfill{}
+
+\caption{ }\label{fig:unnamed-chunk-3}
+\end{figure}
 
@@
 The fractal dimension of a curve can be explained intuitively by thinking of a fractal line as an object too detailed to be one-dimensional, but too simple to be two-dimensional.
-(https://en.wikipedia.org/wiki/Fractal_dimension) Another way to understand this is to consider the process by which the Koch Curve is constructed.
+(\url{https://en.wikipedia.org/wiki/Fractal_dimension}) Another way to understand this is to consider the process by which the Koch Curve is constructed.
 As we continually modulate the object through iterations, we can add an infinite number of additional line segments which create innumerable jagged peaks.
@@
 
-```{r, out.height =  "30%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","morefractals.png"))
-knitr::include_graphics(here::here("paper","paper_images","square.png"))
+\begin{figure}
 
-```
+\includegraphics[width=0.9in,height=0.3\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/morefractals} \hfill{}
+
+\caption{ }\label{fig:unnamed-chunk-4-1}
+\end{figure}
+\begin{figure}
+
+\includegraphics[width=1.71in,height=0.3\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/square} \hfill{}
+
+\caption{ }\label{fig:unnamed-chunk-4-2}
+\end{figure}
 
@@
 One can also calculate a D value, fractal dimension of natural objects like coastlines, the outlines of clouds, or the silhouettes of mountain ranges on the horizon.
-These ideas have been rigorously developed and investigated, exemplified in the University of Oregon’s Dr.
-Richard Taylor theory of Fractal Fluency.
+These ideas have been rigorously developed and investigated, exemplified in the University of Oregon's Dr.~Richard Taylor theory of Fractal Fluency.
 Simply put, human vision has not only adapted to efficiently process and perceive the dimensionality of fractals in nature, but has evolved to prefer fractals of a certain dimensional range.
@@
 Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (Hagerhall), the reduction of stress using fractal art and architecture (Taylor) and even in the experience of hearing fractal melodies (Beauvois).
-There appears to be a clear link between, the fractal’s representation of complexity, the connection with natural objects and processes, and the human mind.
+There appears to be a clear link between, the fractal's representation of complexity, the connection with natural objects and processes, and the human mind.
 
@@
 
-```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","blotches.png"))
-knitr::include_graphics(here::here("paper","paper_images","moreblotches.png"))
-knitr::include_graphics(here::here("paper","paper_images","deconstruction.png"))
+\begin{figure}
 
-```
+\includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/blotches} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/moreblotches} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/deconstruction} \hfill{}
+
+\caption{ }\label{fig:unnamed-chunk-5}
+\end{figure}
 
@@
 
-# Methods
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 The time spent viewing each image was measured as a Dwell Time, following the procedures of Baldwin et.
-al.
-2019.
+al.~2019.
 A set of images were generated for each of fourteen different fractal types iterated from 4 to 9 times.
@@
 
-```{r, fig.show = "hold", out.height =  "25%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","task_outline.jpg"))
-knitr::include_graphics(here::here("paper","paper_images","fractal_direction.png"))
-```
+\begin{figure}
 
-## Participants
+\includegraphics[width=1.71in,height=0.25\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/task_outline} \includegraphics[width=1.71in,height=0.25\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/fractal_direction} \hfill{}
+
+\caption{ }\label{fig:unnamed-chunk-6}
+\end{figure}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
 The study recruited 16 healthy young adults aging from 16-35 through the UO sona system.
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
 
-# Results
+We used R (Version 3.6.3; R Core Team, 2020) and the R-packages \emph{janitor} (Version 2.0.1; Firke, 2020), and \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020) for all our analyses.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 Yet up to this point in time, these studies have utilized static and independent fractal images.
-These studies also have generally employed an alternative forced choice paradigm to quantify participant’s preferences.
+These studies also have generally employed an alternative forced choice paradigm to quantify participant's preferences.
 This study is novel in two ways.
@@
 For this reason we can design studies which use 3 dimensional fractal images and another biologically inspired stimuli type cellular automata.
-Surveys including the Autism Spectrum Quotient, and perceptual tasks like visual search and card sorting can be correlated with dwell time data can be utilized to better understand individual preferences and perceptual proclivities for complexity.
+Surveys including the Autism Spectrum Quotient, and perceptual tasks like visual search and card sorting can be correlated with dwell time data can be utilized to better understand individual preferences and perceptual proclivities for complexity.\\
 This study was the first of its kind, utilizing dynamic fractals presented in a dwell time paradigm.
@@
 
-# Discussion
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 
-# References
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-<div id="refs" custom-style="Bibliography"></div>
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-R-janitor}{}%
+Firke, S. (2020). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
 \endgroup
+
+\end{document}

### 2020-12-07 paper/paper_papaja.rmd
knitted .pdf
updates

@@
     affiliation   : "1"
-    email         : "my@email.com"
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
@@
     institution   : "University of Oregon"
-
-authornote: |
- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
 
@@
 ```{r setup, include = FALSE}
+
+if(!"tinytex" %in% rownames(installed.packages())) install.packages("tinytex")
+tinytex::install_tinytex()
+if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
+devtools::install_github("crsh/papaja")
+
 library(janitor)
@@
 # Introduction
-  Fractal is a term originally derived to describe the “roughness,” (Mandelbrot) of objects, surfaces, or textures.
-Fractal properties are pervasive throughout nature (Losa) and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
+  Fractal is a term originally derived to describe the “roughness,” (@mandelbrot1989fractal) of objects, surfaces, or textures.
+Fractal properties are pervasive throughout nature (@losa2009fractal) and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
 These fractal properties are identified by their self-similarity and scale invariance.
@@
 A secondary analysis of fractal fluency has shown that humans often also prefer fractal images to non-fractal images and that we prefer fractals which more closely resemble natural images to fractals which are geometrically exact.
-(Spehar, and Spies) Extensions on these research findings have led to the use of fractal images in therapeutic applications.
-Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (Hagerhall), the reduction of stress using fractal art and architecture (Taylor) and even in the experience of hearing fractal melodies (Beauvois).
+(@spehar2003universal) Extensions on these research findings have led to the use of fractal images in therapeutic applications.
+Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (@hagerhall2015human), the reduction of stress using fractal art and architecture (@taylor2006reduction) and even in the experience of hearing fractal melodies (@beauvois2007quantifying).
 There appears to be a clear link between, the fractal’s representation of complexity, the connection with natural objects and processes, and the human mind.
@@
 
-## Participants
-The study recruited 16 healthy young adults aging from 16-35 through the UO sona system.
+##Participants
+The study recruited 16 healthy young adults ages 16-35 through the UO SONA recruitment system.  All participants had normal or corrected to normal vision with no history of neurological damage.
 
-## Data analysis
+##Data analysis
 We used `r cite_r("r-references.bib")` for all our analyses.
@@
 
+ A two-way ANOVA was conducted to examin the effect of dwell times on fractal presentation directions.
+The results indicated a significant interaction between the effects of fractal direction and dwell time, *F*(2,31.01) = 42.68, *p*<0.05).
+Simple main effects showed that growth conditions showed significantly longer dwell times compared to the decay or random directional conditions.
+```{r, fig.show = "hold", out.height =  "25%",fig.align = 'left'}
+
+knitr::include_graphics(here::here("presentation_images","group1.png"))
+
+```
+
+  The following graph plots the dwell times over the course of the study for participant group 1.
+Group 1 and 2 where counterbalanced in fractal presentation order but show similar trends of decreasing dwell times as image number increases or the task itself progresses.
+Decreases in dwell times over time are likely attributed to fatigue or waning attention as the participants lose focus over time.
+```{r, fig.show = "hold", out.height =  "25%",fig.align = 'left'}
+
+knitr::include_graphics(here::here("presentation_images","ovr_dwell_time2.png"))
+
+```
+
+# Discussion
+
   In this study a dwell time paradigm which measures looking times of participants as they advance through a self paced slideshow, was used to measure the preferences for fractal images.
 Slideshows were composed of a variety of different fractal types, each of which was presented in a sequential pattern of growth and decay of complexity.
-Fractal images are abundant in nature, and fractal fluency theory (Taylor) has shown that humans have evolved perceptual preferences for fractal images.
+Fractal images are abundant in nature, and fractal fluency theory (@taylor2006reduction) has shown that humans have evolved perceptual preferences for fractal images.
 Previous studies have shown that both adults and children display patterns of aesthetic preference for a particular range of fractal dimension, a mathematical quantification analogous to complexity.
@@
 First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology.
-(Baldwin, Kosie)  By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.
+(@kosie2019attentiona)  By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.
 We suggest that a dwell time paradigm provides a more nuanced insight into aesthetic preference or interest in a given stimuli set.
@@
 Surveys including the Autism Spectrum Quotient, and perceptual tasks like visual search and card sorting can be correlated with dwell time data can be utilized to better understand individual preferences and perceptual proclivities for complexity.
+
   This study was the first of its kind, utilizing dynamic fractals presented in a dwell time paradigm.
 The results from this study have shown that these methods are reliable and informative in regards to research questions which explore and connect fractal fluency, human perception, preference for complexity.
-
-# Discussion
 

### 2020-12-08 paper/paper_papaja.rmd
update again

@@
 Longer dwell times for higher complexity may indicate that human perception is captured by the surprising or novel nature of a fractal’s iterative growth process.
-
 This study is the first to use a novel presentation of dynamic fractal processes to explore fractal fluency and aesthetic preference.
@@
 These findings can be used to develop new techniques for utilizing fractals as therapeutic tools.
-  <!-- https://tinyurl.com/ybremelq -->
 
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "fractals, dwell time, growth sequence, decay sequence"
 
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
 draft             : no
-
 ---
@@
 ```{r setup, include = FALSE}
+knitr::opts_chunk$set(warning = F,
+                      message = F)
 
@@
 # Sys.setenv(LANG = "en")
-```
 
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+library(here)
+library(rio)
+library(knitr)
+library(tidyverse)
+
+theme_set(theme_minimal())
 ```
@@
 # Introduction
-  Fractal is a term originally derived to describe the “roughness,” (@mandelbrot1989fractal) of objects, surfaces, or textures.
-Fractal properties are pervasive throughout nature (@losa2009fractal) and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
+
+  Fractal is a term originally derived to describe the “roughness,” [@mandelbrot1989fractal] of objects, surfaces, or textures.
+Fractal properties are pervasive throughout nature [@losa2009fractal] and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
 These fractal properties are identified by their self-similarity and scale invariance.
@@
 
-```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","coast.jpg"))
-knitr::include_graphics(here::here("paper","paper_images","fractalfern.png"))
-knitr::include_graphics(here::here("paper","paper_images","spooky.png"))
-
+```{r, fig.show = "hold", out.width = "30%",fig.align = 'center'}
+include_graphics(here("paper","paper_images","coast.jpg"))
+include_graphics(here("paper","paper_images","fractalfern.png"))
+include_graphics(here("paper","paper_images","spooky.png"))
 ```
 
-  Scale-invariance is a related mathematical property which can be applied to objects or laws that do not change if scales of length, energy, or other variables, are multiplied by a common factor, and thus represent a universality.
-(wiki, scale invariance)  Expressed more intuitively, scale invariance implies that it does not matter at which scale one views and object or observes a process, because the object or process contains a commonality at all scales.
+  Scale-invariance is a related mathematical property which can be applied to objects that do not change across different scales; there is a similar patterm at all levels of magnification.
+Expressed more intuitively, scale invariance implies that it does not matter at which scale one views and object or observes a process, because the object or process contains a commonality at all scales.
 
@@
 This can be repeated infinitely and often results in high complex objects or systems.
-Fractal mathematics have continued to be developed and utilized in mathematics, physics, biology, chemistry, and engineering.
-A recent application of fractal mathematics is utilized in computer generated images and models.
+Fractal mathematics have continued to be developed and utilized in mathematics, physics, biology, chemistry, and engineering.A recent application of fractal mathematics is utilized in computer generated images and models.
 By starting with a simple algorithm, a mathematical equation or rule, graphic artists and programmers can create highly complex models of natural systems.
@@
 Again, by using the same algorithmic rule, divide a segment into thirds and span the removed middle third with an isosceles angle, and is applied to all four of the line segments created by the first iterative change.
-Now each of these four line segments will include an angular bump or peak that spans their middle third.
-These results in a set of 16 angular connected line segments.
+Now each of these four line segments will include an angular bump or peak that spans their middle third.These results in a set of 16 angular connected line segments.
 Just as we did with the cantor set, and can do with all fractal growth iterations, we can continue applying the rule to the updated condition of the object.
@@
 
-```{r, fig.show = "hold", out.width =  "50%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","bars.png"))
-knitr::include_graphics(here::here("paper","paper_images","star.jpg"))
+```{r, fig.show = "hold", out.width = "50%",fig.align = 'center'}
+include_graphics(here("paper","paper_images","bars.png"))
+include_graphics(here("paper","paper_images","star.jpg"))
+```
 
-```
   There are numerous examples of these types of geometric transformations which result in beautiful and striking constructions.
@@
 
-```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","squigly.jpg"))
-knitr::include_graphics(here::here("paper","paper_images","triangle.jpg"))
-knitr::include_graphics(here::here("paper","paper_images","maze.jpg"))
-
+```{r, fig.show = "hold", out.width = "30%",fig.align = 'center'}
+include_graphics(here("paper","paper_images","squigly.jpg"))
+include_graphics(here("paper","paper_images","triangle.jpg"))
+include_graphics(here("paper","paper_images","maze.jpg"))
 ```
@@
 
-```{r, out.height =  "30%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","morefractals.png"))
-knitr::include_graphics(here::here("paper","paper_images","square.png"))
-
+```{r, out.height = "30%",fig.align = 'center'}
+include_graphics(here("paper","paper_images","morefractals.png"))
+include_graphics(here("paper","paper_images","square.png"))
 ```
@@
 A secondary analysis of fractal fluency has shown that humans often also prefer fractal images to non-fractal images and that we prefer fractals which more closely resemble natural images to fractals which are geometrically exact.
-(@spehar2003universal) Extensions on these research findings have led to the use of fractal images in therapeutic applications.
-Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (@hagerhall2015human), the reduction of stress using fractal art and architecture (@taylor2006reduction) and even in the experience of hearing fractal melodies (@beauvois2007quantifying).
+[@spehar2003universal] Extensions on these research findings have led to the use of fractal images in therapeutic applications.
+Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals [@hagerhall2015human], the reduction of stress using fractal art and architecture [@taylor2006reduction] and even in the experience of hearing fractal melodies [@beauvois2007quantifying].
 There appears to be a clear link between, the fractal’s representation of complexity, the connection with natural objects and processes, and the human mind.
@@
 
-```{r, fig.show = "hold", out.width =  "30%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","blotches.png"))
-knitr::include_graphics(here::here("paper","paper_images","moreblotches.png"))
-knitr::include_graphics(here::here("paper","paper_images","deconstruction.png"))
-
+```{r, fig.show = "hold", out.width = "30%",fig.align = 'center'}
+include_graphics(here("paper","paper_images","blotches.png"))
+include_graphics(here("paper","paper_images","moreblotches.png"))
+include_graphics(here("paper","paper_images","deconstruction.png"))
 ```
@@
   Participants viewed self paced slideshows of fractal images in sequences of iterative growth and decay phases as well as a random ordering.
-The time spent viewing each image was measured as a Dwell Time, following the procedures of Baldwin et.
-al.
+The time spent viewing each image was measured as a Dwell Time, following the procedures of Baldwin et al.
 2019.
@@
 Random slideshows presented the entire set of fractal images in random order.
-6 participants viewed Sequential Slideshow A, starting with Fractal Type 1 to Type 14, and Random Slideshow A starting with Fractal Image 1 to Image 174.
+Six participants viewed Sequential Slideshow A, starting with Fractal Type 1 to Type 14, and Random Slideshow A starting with Fractal Image 1 to Image 174.
 The remaining 10 participants viewed Sequential Slideshow B, starting with Fractal Type 14 to Type 1, and Random Slideshow B starting with Fractal Image 174 to Image 1.
@@
 
-```{r, fig.show = "hold", out.height =  "25%",fig.align = 'left'}
-knitr::include_graphics(here::here("paper","paper_images","task_outline.jpg"))
-knitr::include_graphics(here::here("paper","paper_images","fractal_direction.png"))
+```{r, fig.show = "hold", out.height = "25%",fig.align = 'center'}
+include_graphics(here("paper","paper_images","task_outline.jpg"))
+include_graphics(here("paper","paper_images","fractal_direction.png"))
 ```
 
-##Participants
+## Participants
+
 The study recruited 16 healthy young adults ages 16-35 through the UO SONA recruitment system. All participants had normal or corrected to normal vision with no history of neurological damage.
 
-##Data analysis
+## Data analysis
+
 We used `r cite_r("r-references.bib")` for all our analyses.
@@
 
- A two-way ANOVA was conducted to examin the effect of dwell times on fractal presentation directions.
-The results indicated a significant interaction between the effects of fractal direction and dwell time, *F*(2,31.01) = 42.68, *p*<0.05).
-Simple main effects showed that growth conditions showed significantly longer dwell times compared to the decay or random directional conditions.
-```{r, fig.show = "hold", out.height =  "25%",fig.align = 'left'}
+```{r import_data}
+fractal_data <- clean_names(import(here("data", "frac_total.csv")))
 
-knitr::include_graphics(here::here("presentation_images","group1.png"))
+raw_A <- clean_names(import(here("data", "frac_SA.csv")))
 
+raw_B <- clean_names(import(here("data", "frac_SB.csv")))
 ```
 
-  The following graph plots the dwell times over the course of the study for participant group 1.
+```{r clean_data}
+fractal_data <- fractal_data %>% 
+  pivot_longer(cols = a:p,
+               names_to = "participant",
+               values_to = "dwell_time")
+
+fractal_data <- fractal_data %>% 
+  mutate(direction = factor(direction, labels = c("Decay", "Growth", "Random")),
+         participant = factor(participant),
+         disp_image = factor(disp_image))
+
+fractal_data <- fractal_data %>% 
+  mutate(fractal_type = case_when(
+    grepl("Fern_A", disp_image, fixed = T) ~ "Fern_A",
+    grepl("Fern_B", disp_image, fixed = T) ~ "Fern_B",
+    grepl("Fractal_Curves_A", disp_image, fixed = T) ~ "Fractal_Curves_A",
+    grepl("Fractal_Curves_B", disp_image, fixed = T) ~ "Fractal_Curves_B",
+    grepl("Fractal_Curves_C", disp_image, fixed = T) ~ "Fractal_Curves_C",
+    grepl("Fractal_Curves_D", disp_image, fixed = T) ~ "Fractal_Curves_D",
+    grepl("Fractal_Curves_E", disp_image, fixed = T) ~ "Fractal_Curves_E",
+    grepl("Hilbert", disp_image, fixed = T) ~ "Hilbert",
+    grepl("Moore", disp_image, fixed = T) ~ "Moore",
+    grepl("Pythagoras_A", disp_image, fixed = T) ~ "Pythagoras_A",
+    grepl("Pythagoras_B", disp_image, fixed = T) ~ "Pythagoras_B",
+    grepl("Sierpinski_A", disp_image, fixed = T) ~ "Sierpinski_A",
+    grepl("Sierpinski_B", disp_image, fixed = T) ~ "Sierpinski_B",
+    grepl("Tree_A", disp_image, fixed = T) ~ "Tree_A"
+  ))
+
+fractal_data <- fractal_data %>% 
+  mutate(sequence_position = case_when(
+    grepl("A0.png", disp_image, fixed = T) ~ 1,
+    grepl("B0.png", disp_image, fixed = T) ~ 1,
+    grepl("C0.png", disp_image, fixed = T) ~ 1,
+    grepl("D0.png", disp_image, fixed = T) ~ 1,
+    grepl("E0.png", disp_image, fixed = T) ~ 1,
+    grepl("_0.png", disp_image, fixed = T) ~ 1,
+    grepl("A100.png", disp_image, fixed = T) ~ 2,
+    grepl("B100.png", disp_image, fixed = T) ~ 2,
+    grepl("A1.png", disp_image, fixed = T) ~ 2,
+    grepl("B1.png", disp_image, fixed = T) ~ 2,
+    grepl("C1.png", disp_image, fixed = T) ~ 2,
+    grepl("D1.png", disp_image, fixed = T) ~ 2,
+    grepl("E1.png", disp_image, fixed = T) ~ 2,
+    grepl("_1.png", disp_image, fixed = T) ~ 2,
+    grepl("A200.png", disp_image, fixed = T) ~ 3,
+    grepl("B200.png", disp_image, fixed = T) ~ 3,
+    grepl("A2.png", disp_image, fixed = T) ~ 3,
+    grepl("B2.png", disp_image, fixed = T) ~ 3,
+    grepl("C2.png", disp_image, fixed = T) ~ 3,
+    grepl("D2.png", disp_image, fixed = T) ~ 3,
+    grepl("E2.png", disp_image, fixed = T) ~ 3,
+    grepl("_2.png", disp_image, fixed = T) ~ 3,
+    grepl("A400.png", disp_image, fixed = T) ~ 4,
+    grepl("B400.png", disp_image, fixed = T) ~ 4,
+    grepl("A3.png", disp_image, fixed = T) ~ 4,
+    grepl("B3.png", disp_image, fixed = T) ~ 4,
+    grepl("C3.png", disp_image, fixed = T) ~ 4,
+    grepl("D3.png", disp_image, fixed = T) ~ 4,
+    grepl("E3.png", disp_image, fixed = T) ~ 4,
+    grepl("_3.png", disp_image, fixed = T) ~ 4,
+    grepl("A800.png", disp_image, fixed = T) ~ 5,
+    grepl("B800.png", disp_image, fixed = T) ~ 5,
+    grepl("A4.png", disp_image, fixed = T) ~ 5,
+    grepl("B4.png", disp_image, fixed = T) ~ 5,
+    grepl("C4.png", disp_image, fixed = T) ~ 5,
+    grepl("D4.png", disp_image, fixed = T) ~ 5,
+    grepl("E4.png", disp_image, fixed = T) ~ 5,
+    grepl("_4.png", disp_image, fixed = T) ~ 5,
+    grepl("A1600.png", disp_image, fixed = T) ~ 6,
+    grepl("B1600.png", disp_image, fixed = T) ~ 6,
+    grepl("A5.png", disp_image, fixed = T) ~ 6,
+    grepl("B5.png", disp_image, fixed = T) ~ 6,
+    grepl("C5.png", disp_image, fixed = T) ~ 6,
+    grepl("D5.png", disp_image, fixed = T) ~ 6,
+    grepl("E5.png", disp_image, fixed = T) ~ 6,
+    grepl("_5.png", disp_image, fixed = T) ~ 6,
+    grepl("A3200.png", disp_image, fixed = T) ~ 7,
+    grepl("B3200.png", disp_image, fixed = T) ~ 7,
+    grepl("A6.png", disp_image, fixed = T) ~ 7,
+    grepl("A6400.png", disp_image, fixed = T) ~ 8,
+    grepl("B6400.png", disp_image, fixed = T) ~ 8,
+    grepl("A7.png", disp_image, fixed = T) ~ 8,
+    grepl("A12800.png", disp_image, fixed = T) ~ 9,
+    grepl("B12800.png", disp_image, fixed = T) ~ 9
+  ))
+
+raw_A_long <- raw_A %>% 
+ pivot_longer(cols = a:f, names_to = "participant", values_to = "dwell_time")
+
+raw_B_long <- raw_B %>% 
+ pivot_longer(cols = g:p, names_to = "participant", values_to = "dwell_time")
+```
+
+```{r exclude_outliers}
+cutoff <- mean(fractal_data$dwell_time) + 3 * sd(fractal_data$dwell_time)
+
+filtered_fractal_data <- fractal_data %>% 
+  filter(dwell_time < cutoff)
+```
+
+```{r diff_dwell_time}
+fractal_data_wide <- fractal_data %>% 
+  pivot_wider(names_from = direction,
+              values_from = dwell_time) %>% 
+  select(-Random) %>% 
+  mutate(Growth = unlist(Growth),
+         Decay = unlist(Decay),
+         diff_dwell_time = Growth - Decay)
+```
+
+```{r create_table}
+table_byp <- fractal_data %>% 
+  group_by(participant, direction) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3))
+```
+
+```{r tbyp, results = "asis"}
+apa_table(table_byp, col.names = c("Participant", "Sequence Direction", "Mean Dwell Time (s)", "SD Dwell Time (s)"), caption = "Descriptive statistics of dwell times by participant and direction", note = "Participant means and standard deviations for dwell times by sequence direction (growth, decay, or random).
+All units are in seconds (s).", placement = "htbp")
+```
+
+```{r plots}
+new_data_for_now <- fractal_data %>% 
+  group_by(participant, direction) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3))
+
+new_data_for_later <- fractal_data %>% 
+  group_by(direction) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3),
+            mean_se_dwell_time = round(plotrix::std.error(dwell_time), 3))
+
+ymin = new_data_for_later$mean_dwell_time - new_data_for_later$mean_se_dwell_time
+ymax =new_data_for_later$mean_dwell_time + new_data_for_later$mean_se_dwell_time
+```
+
+  Descriptive statistics for each participant by direction of sequence are shown in Table\ \@ref(tab:tbyp).
+
+```{r main, fig.cap = "Error bars represent standard errors."}
+new_data_for_later %>% 
+  ggplot(aes(x = direction, y = mean_dwell_time, fill = direction)) +
+  geom_col() +
+  labs(x = "Direction", y = "Dwell Time (s)", title = "Dwell Times by Condition") +
+  theme(legend.position = "none") +
+  geom_errorbar(aes(ymin = ymin, ymax = ymax, width = .5)) +
+  scale_fill_viridis_d()
+```
+
+```{r main_model}
+model1 <- lm(data = fractal_data, dwell_time ~ direction)
+
+anova1 <- car::Anova(model1)
+
+anova1a <- apa_print(anova1)
+```
+
+ A one-way ANOVA was conducted to examine the effect of fractal presentation directions on dwell times.
+There was a significant effect of direction on dwell time, `r anova1a$full_result$direction`.
+These results demonstrate that growth conditions showed significantly longer dwell times compared to the decay or random directional conditions.
+These results are depicted in Figure\ \@ref(fig:main).
+
+```{r fractal_type}
+seq_fractal_data <- fractal_data %>% 
+  filter(direction != "Random") %>% 
+  mutate(sequence_position = factor(sequence_position),
+         fractal_type = factor(fractal_type))
+
+new_data_forever <- seq_fractal_data %>% 
+  group_by(sequence_position, fractal_type) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3))
+
+model2 <- lm(data = seq_fractal_data, dwell_time ~ sequence_position * fractal_type)
+
+anova2 <- car::Anova(model2)
+
+anova2a <- apa_print(anova2)
+
+temp <- seq_fractal_data %>% 
+  mutate(seq_pos2 = case_when(
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 1 ~ 18,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 2 ~ 17,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 3 ~ 16,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 4 ~ 15,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 5 ~ 14,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 6 ~ 13,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 7 ~ 12,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 8 ~ 11,
+    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 9 ~ 10,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 1 ~ 1,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 2 ~ 2,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 3 ~ 3,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 4 ~ 4,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 5 ~ 5,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 6 ~ 6,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 7 ~ 7,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 8 ~ 8,
+    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 9 ~ 9,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 1 ~ 12,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 2 ~ 11,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 3 ~ 10,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 4 ~ 9,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 5 ~ 8,
+    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 6 ~ 7,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 1 ~ 1,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 2 ~ 2,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 3 ~ 3,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 4 ~ 4,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 5 ~ 5,
+    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 6 ~ 6,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 1 ~ 16,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 2 ~ 15,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 3 ~ 14,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 4 ~ 13,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 5 ~ 12,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 6 ~ 11,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 7 ~ 10,
+    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 8 ~ 9,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 1 ~ 1,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 2 ~ 2,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 3 ~ 3,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 4 ~ 4,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 5 ~ 5,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 6 ~ 6,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 7 ~ 7,
+    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 8 ~ 8,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 1 ~ 10,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 2 ~ 9,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 3 ~ 8,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 4 ~ 7,
+    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 5 ~ 6,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 1 ~ 1,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 2 ~ 2,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 3 ~ 3,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 4 ~ 4,
+    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 5 ~ 5,
+    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 1 ~ 8,
+    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 2 ~ 7,
+    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 3 ~ 6,
+    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 4 ~ 5,
+    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 1 ~ 1,
+    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 2 ~ 2,
+    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 3 ~ 3,
+    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 4 ~ 4))
+
+new_data_never <- temp %>% 
+  group_by(seq_pos2, fractal_type) %>% 
+  summarise(mean_dwell_time = round(mean(dwell_time), 3),
+            sd_dwell_time = round(sd(dwell_time), 3))
+```
+
+```{r ftfig, fig.cap = "Dwell times by fractal type and sequence position."}
+temp %>% 
+  ggplot(aes(x = seq_pos2, y = dwell_time, color = fractal_type)) +
+  facet_wrap(~fractal_type) +
+  geom_point(data = new_data_never, aes(y = mean_dwell_time)) +
+  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
+  scale_y_continuous(limits = c(0, 1.4)) +
+  geom_line(data = new_data_never, aes(y = mean_dwell_time)) +
+  theme(legend.position = "none") +
+  scale_color_viridis_d()
+```
+
+  Additionally, we conducted a two-way ANOVA with sequence position and fractal type as the factors.
+There was a significant main effect of fractal type, `r anova2a$full_result$fractal_type`, and a main effect of sequence position, `r anova2a$full_result$sequence_position`.
+There was not a significant interaction, `r anova2a$full_result$sequence_position_fractal_type`.
+These results suggest that different fractal types elicit different dwell times, and that dwell times vary significantly by position in the growth-decay sequence, but these effects are independent of one another.
+These results are represented in Figure\ \@ref(fig:ftfig).
+
+```{r fatigue1, fig.cap = "Dwell times over length of entire session for group 1. This group saw the fractal curves first and the tree fractal last."}
+raw_A_long %>% 
+  ggplot(aes(x = number, y = dwell_time, color = participant)) +
+  geom_point(alpha = .6) +
+  geom_smooth(method = "lm", se = F) +
+  labs(title = "Unfolding Dwell Times Over Duration of Task", subtitle = "Group 1: Fractal Curves -> Tree Fractal", x = "Image Number (for entire task)", y = "Dwell Time (s)", color = "Participant")
+```
+
+```{r fatigue2, fig.cap = "Dwell times over length of entire session for group 2. This group saw the tree fractal first and the fractal curves last."}
+raw_B_long %>% 
+  ggplot(aes(x = number, y = dwell_time, color = participant)) +
+  geom_point(alpha = .6) +
+  geom_smooth(method = "lm", se = F) +
+  labs(title = "Unfolding Dwell Times Over Duration of Task", subtitle = "Group 2: Tree Fractal -> Fractal Curves", x = "Image Number (for entire task)", y = "Dwell Time (s)", color = "Participant")
+```
+
+  Figure\ \@ref(fig:fatigue1) plots the dwell times over the course of the study for participant group 1, and Figure\ \@ref(fig:fatigue2) plots the dwell times over the course of the study for group 2.
 Group 1 and 2 where counterbalanced in fractal presentation order but show similar trends of decreasing dwell times as image number increases or the task itself progresses.
 Decreases in dwell times over time are likely attributed to fatigue or waning attention as the participants lose focus over time.
-```{r, fig.show = "hold", out.height =  "25%",fig.align = 'left'}
-
-knitr::include_graphics(here::here("presentation_images","ovr_dwell_time2.png"))
-
-```
 
@@
 Slideshows were composed of a variety of different fractal types, each of which was presented in a sequential pattern of growth and decay of complexity.
-Fractal images are abundant in nature, and fractal fluency theory (@taylor2006reduction) has shown that humans have evolved perceptual preferences for fractal images.
+Fractal images are abundant in nature, and fractal fluency theory [@taylor2006reduction] has shown that humans have evolved perceptual preferences for fractal images.
 Previous studies have shown that both adults and children display patterns of aesthetic preference for a particular range of fractal dimension, a mathematical quantification analogous to complexity.
@@
 This study is novel in two ways.
-First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology.
-(@kosie2019attentiona)  By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.
+First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology [@kosie2019attentiona].
+By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.
 We suggest that a dwell time paradigm provides a more nuanced insight into aesthetic preference or interest in a given stimuli set.

### 2020-12-08 paper/paper_papaja.tex
update again

@@
             pdftitle={Fractals are Cool},
-            pdfkeywords={keywords},
+            pdfauthor={Ben Chaloupka1, Tesufuai Sameshima1, \& Scott Wallner1},
+            pdfkeywords={fractals, dwell time, growth sequence, decay sequence},
             pdfborder={0 0 0},
@@
   {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
 \makeatother
 \shorttitle{Everything is Fractal}
-\author{Ben Chaloupka\textsuperscript{1}, Tesufuai Sameshima\textsuperscript{1}, \& Scott Wallner\textsuperscript{1}}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} University of Oregon}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{fractals, dwell time, growth sequence, decay sequence}
 \usepackage{dblfloatfix}
 
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 \title{Fractals are Cool}
+\author{Ben Chaloupka\textsuperscript{1}, Tesufuai Sameshima\textsuperscript{1}, \& Scott Wallner\textsuperscript{1}}
+\date{}
 
-\date{}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Oregon}
 
@@
 Longer dwell times for higher complexity may indicate that human perception is captured by the surprising or novel nature of a fractal's iterative growth process.
-
 This study is the first to use a novel presentation of dynamic fractal processes to explore fractal fluency and aesthetic preference.
@@
 
-Fractal is a term originally derived to describe the \enquote{roughness,} (Mandelbrot) of objects, surfaces, or textures.
-Fractal properties are pervasive throughout nature (Losa) and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
+Fractal is a term originally derived to describe the \enquote{roughness,} (Mandelbrot, 1989) of objects, surfaces, or textures.
+Fractal properties are pervasive throughout nature (Losa, 2009) and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
 These fractal properties are identified by their self-similarity and scale invariance.
@@
 
-\includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/coast} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/fractalfern} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/spooky} \hfill{}
+{\centering \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/coast} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/fractalfern} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/spooky}
+
+}
 
@@
 
-Scale-invariance is a related mathematical property which can be applied to objects or laws that do not change if scales of length, energy, or other variables, are multiplied by a common factor, and thus represent a universality.
-(wiki, scale invariance) Expressed more intuitively, scale invariance implies that it does not matter at which scale one views and object or observes a process, because the object or process contains a commonality at all scales.
+Scale-invariance is a related mathematical property which can be applied to objects that do not change across different scales; there is a similar patterm at all levels of magnification.
+Expressed more intuitively, scale invariance implies that it does not matter at which scale one views and object or observes a process, because the object or process contains a commonality at all scales.
 
@@
 
-\includegraphics[width=0.5\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/bars} \includegraphics[width=0.5\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/star} \hfill{}
+{\centering \includegraphics[width=0.5\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/bars} \includegraphics[width=0.5\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/star}
+
+}
 
@@
 
-\includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/squigly} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/triangle} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/maze} \hfill{}
+{\centering \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/squigly} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/triangle} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/maze}
+
+}
 
@@
 
-\includegraphics[width=0.9in,height=0.3\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/morefractals} \hfill{}
+{\centering \includegraphics[width=0.9in,height=0.3\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/morefractals}
+
+}
 
@@
 
-\includegraphics[width=1.71in,height=0.3\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/square} \hfill{}
+{\centering \includegraphics[width=1.71in,height=0.3\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/square}
+
+}
 
@@
 A secondary analysis of fractal fluency has shown that humans often also prefer fractal images to non-fractal images and that we prefer fractals which more closely resemble natural images to fractals which are geometrically exact.
-(Spehar, and Spies) Extensions on these research findings have led to the use of fractal images in therapeutic applications.
-Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (Hagerhall), the reduction of stress using fractal art and architecture (Taylor) and even in the experience of hearing fractal melodies (Beauvois).
+(Spehar, Clifford, Newell, \& Taylor, 2003) Extensions on these research findings have led to the use of fractal images in therapeutic applications.
+Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (Hagerhall et al., 2015), the reduction of stress using fractal art and architecture (Taylor, 2006) and even in the experience of hearing fractal melodies (Beauvois, 2007).
 There appears to be a clear link between, the fractal's representation of complexity, the connection with natural objects and processes, and the human mind.
@@
 
-\includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/blotches} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/moreblotches} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/deconstruction} \hfill{}
+{\centering \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/blotches} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/moreblotches} \includegraphics[width=0.3\linewidth]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/deconstruction}
+
+}
 
@@
 Participants viewed self paced slideshows of fractal images in sequences of iterative growth and decay phases as well as a random ordering.
-The time spent viewing each image was measured as a Dwell Time, following the procedures of Baldwin et.
-al.~2019.
+The time spent viewing each image was measured as a Dwell Time, following the procedures of Baldwin et al.~2019.
 A set of images were generated for each of fourteen different fractal types iterated from 4 to 9 times.
@@
 
-\includegraphics[width=1.71in,height=0.25\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/task_outline} \includegraphics[width=1.71in,height=0.25\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/fractal_direction} \hfill{}
+{\centering \includegraphics[width=1.71in,height=0.25\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/task_outline} \includegraphics[width=1.71in,height=0.25\textheight]{/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/paper/paper_images/fractal_direction}
+
+}
 
@@
 
-The study recruited 16 healthy young adults aging from 16-35 through the UO sona system.
+The study recruited 16 healthy young adults ages 16-35 through the UO SONA recruitment system. All participants had normal or corrected to normal vision with no history of neurological damage.
 
@@
 
-We used R (Version 3.6.3; R Core Team, 2020) and the R-packages \emph{janitor} (Version 2.0.1; Firke, 2020), and \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020) for all our analyses.
+We used R (Version 3.6.3; R Core Team, 2019) and the R-packages \emph{\}here} {[}@\}R-here{]}, \emph{dplyr} (Version 1.0.2; Wickham et al., 2020), \emph{forcats} (Version 0.5.0; Wickham, 2020a), \emph{ggplot2} (Version 3.3.2; Wickham, 2016), \emph{janitor} (Version 2.0.1; Firke, 2020), \emph{knitr} (Version 1.30; Xie, 2015), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 1.4.0; Wickham \& Hester, 2020), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.4; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.1.2; Wickham, 2020b), and \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019) for all our analyses.
 
@@
 
+\begin{table*}[htbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tbyp}Descriptive statistics of dwell times by participant and direction}
+
+\begin{tabular}{llll}
+\toprule
+Participant & Sequence Direction & Mean Dwell Time (s) & SD Dwell Time (s)\\
+\midrule
+a & Decay & 1.41 & 1.15\\
+a & Growth & 3.44 & 1.91\\
+a & Random & 1.48 & 1.08\\
+b & Decay & 1.16 & 0.50\\
+b & Growth & 1.56 & 0.96\\
+b & Random & 0.75 & 0.33\\
+c & Decay & 0.62 & 0.13\\
+c & Growth & 0.70 & 0.23\\
+c & Random & 0.78 & 0.26\\
+d & Decay & 0.42 & 0.12\\
+d & Growth & 0.45 & 0.18\\
+d & Random & 0.52 & 0.15\\
+e & Decay & 0.76 & 0.12\\
+e & Growth & 0.78 & 0.12\\
+e & Random & 0.82 & 0.11\\
+f & Decay & 0.75 & 0.14\\
+f & Growth & 0.79 & 0.14\\
+f & Random & 0.75 & 0.12\\
+g & Decay & 0.60 & 0.07\\
+g & Growth & 0.61 & 0.08\\
+g & Random & 0.73 & 0.18\\
+h & Decay & 0.45 & 0.11\\
+h & Growth & 0.47 & 0.12\\
+h & Random & 0.62 & 0.14\\
+i & Decay & 1.21 & 0.42\\
+i & Growth & 1.23 & 0.31\\
+i & Random & 1.12 & 0.34\\
+j & Decay & 0.81 & 0.18\\
+j & Growth & 0.88 & 0.20\\
+j & Random & 1.33 & 0.33\\
+k & Decay & 0.84 & 0.13\\
+k & Growth & 0.92 & 0.19\\
+k & Random & 1.27 & 0.52\\
+l & Decay & 0.59 & 0.17\\
+l & Growth & 0.74 & 0.23\\
+l & Random & 0.73 & 0.23\\
+m & Decay & 0.75 & 0.31\\
+m & Growth & 1.01 & 0.32\\
+m & Random & 0.65 & 0.15\\
+n & Decay & 0.49 & 0.11\\
+n & Growth & 0.57 & 0.15\\
+n & Random & 0.72 & 0.17\\
+o & Decay & 0.42 & 0.06\\
+o & Growth & 0.43 & 0.07\\
+o & Random & 0.41 & 0.04\\
+p & Decay & 0.49 & 0.11\\
+p & Growth & 0.57 & 0.15\\
+p & Random & 1.01 & 0.19\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Participant means and standard deviations for dwell times by sequence direction (growth, decay, or random). All units are in seconds (s).}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table*}
+
+Descriptive statistics for each participant by direction of sequence are shown in Table~\ref{tab:tbyp}.
+
+\begin{figure}
+\centering
+\includegraphics{paper_papaja_files/figure-latex/main-1.pdf}
+\caption{\label{fig:main}Error bars represent standard errors.}
+\end{figure}
+
+A one-way ANOVA was conducted to examine the effect of fractal presentation directions on dwell times.
+There was a significant effect of direction on dwell time, \(F(2, 5,565) = 42.68\), \(\mathit{MSE} = 0.36\), \(p < .001\), \(\hat{\eta}^2_G = .015\).
+These results demonstrate that growth conditions showed significantly longer dwell times compared to the decay or random directional conditions.
+These results are depicted in Figure~\ref{fig:main}.
+
+\begin{figure}
+\centering
+\includegraphics{paper_papaja_files/figure-latex/ftfig-1.pdf}
+\caption{\label{fig:ftfig}Dwell times by fractal type and sequence position.}
+\end{figure}
+
+Additionally, we conducted a two-way ANOVA with sequence position and fractal type as the factors.
+There was a significant main effect of fractal type, \(F(13, 2,697) = 2.30\), \(\mathit{MSE} = 0.53\), \(p = .005\), \(\hat{\eta}^2_G = .011\), and a main effect of sequence position, \(F(8, 2,697) = 2.02\), \(\mathit{MSE} = 0.53\), \(p = .041\), \(\hat{\eta}^2_G = .006\).
+There was not a significant interaction, \(F(65, 2,697) = 0.37\), \(\mathit{MSE} = 0.53\), \(p > .999\), \(\hat{\eta}^2_G = .009\).
+These results suggest that different fractal types elicit different dwell times, and that dwell times vary significantly by position in the growth-decay sequence, but these effects are independent of one another.
+These results are represented in Figure~\ref{fig:ftfig}.
+
+\begin{figure}
+\centering
+\includegraphics{paper_papaja_files/figure-latex/fatigue1-1.pdf}
+\caption{\label{fig:fatigue1}Dwell times over length of entire session for group 1. This group saw the fractal curves first and the tree fractal last.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{paper_papaja_files/figure-latex/fatigue2-1.pdf}
+\caption{\label{fig:fatigue2}Dwell times over length of entire session for group 2. This group saw the tree fractal first and the fractal curves last.}
+\end{figure}
+
+Figure~\ref{fig:fatigue1} plots the dwell times over the course of the study for participant group 1, and Figure~\ref{fig:fatigue2} plots the dwell times over the course of the study for group 2.
+Group 1 and 2 where counterbalanced in fractal presentation order but show similar trends of decreasing dwell times as image number increases or the task itself progresses.
+Decreases in dwell times over time are likely attributed to fatigue or waning attention as the participants lose focus over time.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
 In this study a dwell time paradigm which measures looking times of participants as they advance through a self paced slideshow, was used to measure the preferences for fractal images.
 Slideshows were composed of a variety of different fractal types, each of which was presented in a sequential pattern of growth and decay of complexity.
-Fractal images are abundant in nature, and fractal fluency theory (Taylor) has shown that humans have evolved perceptual preferences for fractal images.
+Fractal images are abundant in nature, and fractal fluency theory (Taylor, 2006) has shown that humans have evolved perceptual preferences for fractal images.
 Previous studies have shown that both adults and children display patterns of aesthetic preference for a particular range of fractal dimension, a mathematical quantification analogous to complexity.
@@
 This study is novel in two ways.
-First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology.
-(Baldwin, Kosie) By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.
+First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology ({\textbf{???}}).
+By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.
 We suggest that a dwell time paradigm provides a more nuanced insight into aesthetic preference or interest in a given stimuli set.
@@
 For this reason we can design studies which use 3 dimensional fractal images and another biologically inspired stimuli type cellular automata.
-Surveys including the Autism Spectrum Quotient, and perceptual tasks like visual search and card sorting can be correlated with dwell time data can be utilized to better understand individual preferences and perceptual proclivities for complexity.\\
+Surveys including the Autism Spectrum Quotient, and perceptual tasks like visual search and card sorting can be correlated with dwell time data can be utilized to better understand individual preferences and perceptual proclivities for complexity.
+
 This study was the first of its kind, utilizing dynamic fractals presented in a dwell time paradigm.
 The results from this study have shown that these methods are reliable and informative in regards to research questions which explore and connect fractal fluency, human perception, preference for complexity.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
 
@@
 
+\leavevmode\hypertarget{ref-beauvois2007quantifying}{}%
+Beauvois, M. W. (2007). Quantifying aesthetic preference and perceived complexity for fractal melodies. \emph{Music Perception}, \emph{24}(3), 247--264.
+
+\leavevmode\hypertarget{ref-R-rio}{}%
+Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.
+
 \leavevmode\hypertarget{ref-R-janitor}{}%
@@
 
+\leavevmode\hypertarget{ref-hagerhall2015human}{}%
+Hagerhall, C., Laike, T., Kuller, M., Marcheschi, E., Boydston, C., \& Taylor, R.
+(2015).
+Human physiological benefits of viewing nature: EEG responses to exact and statistical fractal patterns.
+\emph{Nonlinear Dynamics, Psychology, and Life Sciences}, \emph{19}(1), 1--12.
+
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-losa2009fractal}{}%
+Losa, G. A. (2009). The fractal geometry of life. In \emph{Biology forum/rivista di biologia} (Vol. 102).
+
+\leavevmode\hypertarget{ref-mandelbrot1989fractal}{}%
+Mandelbrot, B. B. (1989). Fractal geometry: What is it, and what does it do? \emph{Proceedings of the Royal Society of London. A. Mathematical and Physical Sciences}, \emph{423}(1864), 3--16.
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
 \leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-spehar2003universal}{}%
+Spehar, B., Clifford, C. W., Newell, B. R., \& Taylor, R. P. (2003). Universal aesthetic of fractals. \emph{Computers \& Graphics}, \emph{27}(5), 813--820.
+
+\leavevmode\hypertarget{ref-taylor2006reduction}{}%
+Taylor, R. P. (2006). Reduction of physiological stress using fractal art and architecture. \emph{Leonardo}, \emph{39}(3), 245--251.
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2020a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H. (2020b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the tidyverse.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-R-knitr}{}%
+Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.org/knitr/}
 

### 2020-12-08 paper/paper_papaja.rmd
fixed references

@@
   Participants viewed self paced slideshows of fractal images in sequences of iterative growth and decay phases as well as a random ordering.
-The time spent viewing each image was measured as a Dwell Time, following the procedures of Baldwin et al.
-2019.
+The time spent viewing each image was measured as a Dwell Time, following the procedures of @hard2019attention and @kosie2019attentional.
 A set of images were generated for each of fourteen different fractal types iterated from 4 to 9 times.
@@
 This study is novel in two ways.
-First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology [@kosie2019attentiona].
+First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology [@kosie2019attentional].
 By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.

### 2020-12-08 paper/paper_papaja.tex
fixed references

@@
 Participants viewed self paced slideshows of fractal images in sequences of iterative growth and decay phases as well as a random ordering.
-The time spent viewing each image was measured as a Dwell Time, following the procedures of Baldwin et al.~2019.
+The time spent viewing each image was measured as a Dwell Time, following the procedures of Hard, Meyer, and Baldwin (2019) and Kosie and Baldwin (2019).
 A set of images were generated for each of fourteen different fractal types iterated from 4 to 9 times.
@@
 This study is novel in two ways.
-First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology ({\textbf{???}}).
+First, we utilize the dwell time paradigm, a robust and reliable task which has been used in statistical learning and event processing studies in developmental psychology (Kosie \& Baldwin, 2019).
 By measuring the time participants look at, or dwell on each image, patterns in preference, curiosity, or surprise can be mapped within or across individuals as they rapidly view many images sequentially.
@@
 
+\leavevmode\hypertarget{ref-hard2019attention}{}%
+Hard, B. M., Meyer, M., \& Baldwin, D. (2019). Attention reorganizes as structure is detected in dynamic action. \emph{Memory \& Cognition}, \emph{47}(1), 17--32.
+
 \leavevmode\hypertarget{ref-R-purrr}{}%
 Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-kosie2019attentional}{}%
+Kosie, J. E., \& Baldwin, D. (2019). Attentional profiles linked to event segmentation are robust to missing information. \emph{Cognitive Research: Principles and Implications}, \emph{4}(1), 1--18.
 

### 2020-12-08 paper/paper_papaja.rmd
Final update?

@@
 The experience of fractals in a number of domains have proven to be therapeutically useful.
-Previous studies have used independent and static fractal images to investigate the relationship between, fractals, complexity and human perception.
+Previous studies have used independent and static fractal images to investigate the relationship between fractals, complexity and human perception.
 This study employs a Dwell Time Paradigm to present self paced slide shows of dynamic fractals in an unfolding process of iterative growth and decay.
-Results of measured looking or dwell times show that participants prefer viewing fractals as they grow through phases of increasing complexity compared to decay phases of decreasing complexity.
+Results of measured looking, or dwell times, show that participants prefer viewing fractals as they grow through phases of increasing complexity compared to decay phases of decreasing complexity.
 Longer dwell times for higher complexity may indicate that human perception is captured by the surprising or novel nature of a fractal’s iterative growth process.
 This study is the first to use a novel presentation of dynamic fractal processes to explore fractal fluency and aesthetic preference.
-Results from 16 participants prove that dynamic fractals can be integrated into the well established dwell time paradigm.
+Results from 16 participants demonstrate that dynamic fractals can be integrated into the well-established dwell time paradigm.
 These findings can be used to develop new techniques for utilizing fractals as therapeutic tools.
@@
 
-  Fractal is a term originally derived to describe the “roughness,” [@mandelbrot1989fractal] of objects, surfaces, or textures.
-Fractal properties are pervasive throughout nature [@losa2009fractal] and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
+  Fractal is a term originally derived to describe the “roughness” of objects, surfaces, or textures [@mandelbrot1989fractal].
+Fractal properties are pervasive throughout nature and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, and in the meandering shape of rivers and blood vessels [@losa2009fractal].
 These fractal properties are identified by their self-similarity and scale invariance.
 Self-similarity implies that a part of the structure maintains the same structure or pattern as the whole.
-For example, if one were to zoom in on a small stretch of coastline, the jagged edges would look similar to the jaggedness of the coastline from a broader view.
-Likewise, a small section of a fern is nearly identical to the branching shape of the entire fern.
+For example, if one were to zoom in on a small stretch of coastline, the jagged edges would look similar to the jaggedness of the coastline from a broader view (Figure\ \@ref(fig:examples)).
+Likewise, a small section of a fern is nearly identical to the branching shape of the entire fern (Figure\ \@ref(fig:examples)).
 
-```{r, fig.show = "hold", out.width = "30%",fig.align = 'center'}
+```{r examples, fig.show = "hold", out.width = "30%",fig.align = 'center', fig.cap = "Examples of fractals in nature. From left to right: coastline, fern, tree branches."}
 include_graphics(here("paper","paper_images","coast.jpg"))
@@
 A crystal starts with a tiny bit of structure, and that structure is repeated, growing on itself using the same pattern or rule for growth.
-This can be seen quite obviously in objects that are themselves fractals, such as the branching process of trees, but other natural processes follow the rules of fractals.
+This can be seen quite obviously in objects that are themselves fractals, such as the branching process of trees (Figure\ \@ref(fig:examples)), but other natural processes follow the rules of fractals.
 Hurricanes, avalanches, the diffusion of molecules in solution, the dissolving of porous rock, the electrical breakdown of dialectics, and in the growth of our lungs and brains.
-Strikingly fractal properties can be found in statistical systems or distributions of word usage, foraging behaviors, rock size and in the frequency of scientific journal citations, and network outages of the internet.
-(Wiki, scale invariance) The underlying principle of fractals is that a simple process can through infinitely many iterations to become a very complex process.
+Strikingly fractal properties can be found in statistical systems, distributions of word usage, foraging behaviors, rock size, the frequency of scientific journal citations, and network outages of the internet.
+The underlying principle of fractals is that a simple process can, through infinitely many iterations, become a very complex process.
 Many processes which involve bifurcation, splitting, replication and growth can be fractal mathematics and geometry.
-Fractal mathematics can model these complex systems by searching for the simple rules or laws that drive these processes.
-(http://pages.cs.wisc.edu/~ergreen/honors_thesis/fractal.html)
+Fractal mathematics can model these complex systems by searching for the simple rules or laws that drive these processes (http://pages.cs.wisc.edu/~ergreen/honors_thesis/fractal.html).
 
@@
 These iterative processes essentially use a rule to take an initial condition or state, change or modulate it, then put the resulting updated state back into the rule to generate another new state.
-This can be repeated infinitely and often results in high complex objects or systems.
-Fractal mathematics have continued to be developed and utilized in mathematics, physics, biology, chemistry, and engineering.A recent application of fractal mathematics is utilized in computer generated images and models.
-By starting with a simple algorithm, a mathematical equation or rule, graphic artists and programmers can create highly complex models of natural systems.
+This can be repeated infinitely and often results in highly complex objects or systems.
+Fractal mathematics have continued to be developed and utilized in mathematics, physics, biology, chemistry, and engineering.
+A recent application of fractal mathematics is utilized in computer-generated images and models.
+By starting with a simple algorithm, mathematical equation, or rule, graphic artists and programmers can create highly complex models of natural systems.
 
@@
 
-  Two premiere examples of these mathematical or statistical fractals can be seen in the Koch Curve and the Cantor Set.
+  Two premiere examples of these mathematical or statistical fractals can be seen in the Koch Curve and the Cantor Set, seen in Figure\ \@ref(fig:kochcantor).
 In each case an image is created by starting with a single line segment and a rule for changing that line segment.
@@
 
-```{r, fig.show = "hold", out.width = "50%",fig.align = 'center'}
+```{r kochcantor, fig.show = "hold", out.width = "50%",fig.align = 'center', fig.cap = "Top: Cantor Set. Bottom: Koch Curve."}
 include_graphics(here("paper","paper_images","bars.png"))
@@
   There are numerous examples of these types of geometric transformations which result in beautiful and striking constructions.
-Some well known fractal geometries are known as, The Dragon Curve, Sierpinski Triangle, and Hilbert Curve.
+Some well known fractal geometries are known as The Dragon Curve, Sierpinski Triangle, and Hilbert Curve, depicted in Figure\ \@ref(fig:threees).
 These examples show the diversity of implementations of fractal properties in geometry.
@@
 
-```{r, fig.show = "hold", out.width = "30%",fig.align = 'center'}
+```{r threees, fig.show = "hold", out.width = "30%",fig.align = 'center', fig.cap = "Left to right: Dragon Curve, Sierpinski Triangle, and Hilbert Curve."}
 include_graphics(here("paper","paper_images","squigly.jpg"))
@@
 A fractal like the Dragon Curve or Koch Curve can have a dimensionality between 1 and 2, such as 1.2, 1.5, or 1.74823.
-At first this concept feels counter intuitive.
-The non-integer dimensionality occurs because the length of the curve between any two points on the Koch snowflake is effectively infinite.
+At first this concept feels counter-intuitive.
+The non-integer dimensionality occurs because the length of the curve between any two points on the Koch snowflake is effectively infinite (Figure\ \@ref(fig:snowflake)).
 No small piece of it is line-like, but rather it is composed of an infinite number of segments joined at different angles.
@@
 
-```{r, out.height = "30%",fig.align = 'center'}
+```{r snowflake, out.height = "30%",fig.align = 'center', fig.cap="Koch Snowflake."}
 include_graphics(here("paper","paper_images","morefractals.png"))
+```
+
+```{r cube, out.height = "30%",fig.align = 'center', fig.cap="Fractal with dimensionality between 2 and 3."}
 include_graphics(here("paper","paper_images","square.png"))
@@
 Using fractal mathematics invented by Mandelbrot, we can calculate the dimensionality of any fractal including the Koch and Dragon Curves which have dimensionalities of 1.262 and 1.5236 respectively.
-Similarly an object which begins as a two dimensional fractal, can be iterated to grow into the third dimension and have a calculated dimension between 2 and 3.
+Similarly an object which begins as a two dimensional fractal, can be iterated to grow into the third dimension and have a calculated dimension between 2 and 3 (Figure\ \@ref(fig:cube)).
 Thus, dimensionality can be considered as the space filling capacity of a fractal.
@@
 Participants select the fractal image they prefer aesthetically and after viewing many pairs with differing dimensions, statistics are used to calculate the most preferred dimensionality range across participants.
-The overarching results of previous research have shown that humans, both adults and children prefer fractals within a range of dimensions that coincide with the fractal dimension that is found in natural objects and scenes, usually between 1.3 and 1.5.Remembering that fractal dimension is an analog for complexity, we can conclude that most humans prefer a moderate level of complexity compared to low or high complexity near the extremes.
-A secondary analysis of fractal fluency has shown that humans often also prefer fractal images to non-fractal images and that we prefer fractals which more closely resemble natural images to fractals which are geometrically exact.
-[@spehar2003universal] Extensions on these research findings have led to the use of fractal images in therapeutic applications.
-Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals [@hagerhall2015human], the reduction of stress using fractal art and architecture [@taylor2006reduction] and even in the experience of hearing fractal melodies [@beauvois2007quantifying].
+The overarching results of previous research have shown that humans, both adults and children prefer fractals within a range of dimensions that coincide with the fractal dimension that is found in natural objects and scenes, usually between 1.3 and 1.5.
+Remembering that fractal dimension is an analog for complexity, we can conclude that most humans prefer a moderate level of complexity compared to low or high complexity near the extremes.
+A secondary analysis of fractal fluency has shown that humans often also prefer fractal images to non-fractal images and that we prefer fractals which more closely resemble natural images to fractals which are geometrically exact [Figure\ \@ref(fig:natural), @spehar2003universal].
+Extensions on these research findings have led to the use of fractal images in therapeutic applications.
+Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals [@hagerhall2015human], the reduction of stress using fractal art and architecture [@taylor2006reduction], and even in the experience of hearing fractal melodies [@beauvois2007quantifying].
 There appears to be a clear link between, the fractal’s representation of complexity, the connection with natural objects and processes, and the human mind.
@@
 
-```{r, fig.show = "hold", out.width = "30%",fig.align = 'center'}
+```{r natural, fig.show = "hold", out.width = "30%",fig.align = 'center', fig.cap="Fractals that closely resemble natural scenes."}
 include_graphics(here("paper","paper_images","blotches.png"))
@@
 
-  However our natural experience of the world is not so static, fragmented and simple, it is often dynamic, cohesive and alive.
+  However, our natural experience of the world is not so static, fragmented, and simple; it is often dynamic, cohesive, and alive.
 To create a more lifelike experience of fractals we present participants with the unfolding process of a fractal as it is iterated through its process of changing in complexity.
@@
 A set of images were generated for each of fourteen different fractal types iterated from 4 to 9 times.
-Each participant viewed a sequential slideshow and a random slideshow.
+Each participant viewed a sequential slideshow and a random slideshow (Figure\ \@ref(fig:task)).
 Sequential slideshows presented each fractal type through phases of growth and decay from the least complex to most complex iterations and back down from most complex to least complex.
@@
 
-```{r, fig.show = "hold", out.height = "25%",fig.align = 'center'}
+```{r task, fig.show = "hold", out.height = "25%",fig.align = 'center', fig.cap="Task design."}
 include_graphics(here("paper","paper_images","task_outline.jpg"))
@@
 anova1a <- apa_print(anova1)
+
+pairwise1 <- pairwise.t.test(fractal_data$dwell_time, fractal_data$direction)
+
+pairwise1a <- as.data.frame(pairwise1$p.value)
 ```
@@
 There was a significant effect of direction on dwell time, `r anova1a$full_result$direction`.
-These results demonstrate that growth conditions showed significantly longer dwell times compared to the decay or random directional conditions.
+Pairwise comparisons revealed that there was a significant difference between growth and decay sequences, *p* < .001, growth and random sequences, *p* < .001, and random and decay sequences, *p* < .001.
+These results demonstrate that participants spent the most time viewing fractals during the growth phase and the least time during the decay phase.
 These results are depicted in Figure\ \@ref(fig:main).
@@
 
-  In this study a dwell time paradigm which measures looking times of participants as they advance through a self paced slideshow, was used to measure the preferences for fractal images.
+  In this study, a dwell time paradigm which measures looking times of participants as they advance through a self paced slideshow was used to measure the preferences for fractal images.
 Slideshows were composed of a variety of different fractal types, each of which was presented in a sequential pattern of growth and decay of complexity.
-Fractal images are abundant in nature, and fractal fluency theory [@taylor2006reduction] has shown that humans have evolved perceptual preferences for fractal images.
+Fractal images are abundant in nature, and fractal fluency theory has shown that humans have evolved perceptual preferences for fractal images [@taylor2006reduction].
 Previous studies have shown that both adults and children display patterns of aesthetic preference for a particular range of fractal dimension, a mathematical quantification analogous to complexity.
@@
 But often our experiences of natural scenes are not static or independent, like the stimuli which has been used in all previous studies.
-To better replicate natural experiences this study utilized a slideshow of fractal images which iterate through phases of growing and decaying complexity.
+To better replicate natural experiences, this study utilized a slideshow of fractal images which iterate through phases of growing and decaying complexity.
 We sought to investigate whether participants would prefer dynamic fractals as they grow or decay in complexity.

### 2020-12-08 paper/paper_papaja.tex
Final update?

@@
 The experience of fractals in a number of domains have proven to be therapeutically useful.
-Previous studies have used independent and static fractal images to investigate the relationship between, fractals, complexity and human perception.
+Previous studies have used independent and static fractal images to investigate the relationship between fractals, complexity and human perception.
 This study employs a Dwell Time Paradigm to present self paced slide shows of dynamic fractals in an unfolding process of iterative growth and decay.
-Results of measured looking or dwell times show that participants prefer viewing fractals as they grow through phases of increasing complexity compared to decay phases of decreasing complexity.
+Results of measured looking, or dwell times, show that participants prefer viewing fractals as they grow through phases of increasing complexity compared to decay phases of decreasing complexity.
 Longer dwell times for higher complexity may indicate that human perception is captured by the surprising or novel nature of a fractal's iterative growth process.
 This study is the first to use a novel presentation of dynamic fractal processes to explore fractal fluency and aesthetic preference.
-Results from 16 participants prove that dynamic fractals can be integrated into the well established dwell time paradigm.
+Results from 16 participants demonstrate that dynamic fractals can be integrated into the well-established dwell time paradigm.
 These findings can be used to develop new techniques for utilizing fractals as therapeutic tools.
@@
 
-Fractal is a term originally derived to describe the \enquote{roughness,} (Mandelbrot, 1989) of objects, surfaces, or textures.
-Fractal properties are pervasive throughout nature (Losa, 2009) and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, in the meandering shape of rivers and blood vessels.
+Fractal is a term originally derived to describe the \enquote{roughness} of objects, surfaces, or textures (Mandelbrot, 1989).
+Fractal properties are pervasive throughout nature and can be identified in the texture of clouds and mountains, in the branching pattern of trees and lightning, and in the meandering shape of rivers and blood vessels (Losa, 2009).
 These fractal properties are identified by their self-similarity and scale invariance.
 Self-similarity implies that a part of the structure maintains the same structure or pattern as the whole.
-For example, if one were to zoom in on a small stretch of coastline, the jagged edges would look similar to the jaggedness of the coastline from a broader view.
-Likewise, a small section of a fern is nearly identical to the branching shape of the entire fern.
+For example, if one were to zoom in on a small stretch of coastline, the jagged edges would look similar to the jaggedness of the coastline from a broader view (Figure~\ref{fig:examples}).
+Likewise, a small section of a fern is nearly identical to the branching shape of the entire fern (Figure~\ref{fig:examples}).
 
@@
 
-\caption{ }\label{fig:unnamed-chunk-1}
+\caption{Examples of fractals in nature. From left to right: coastline, fern, tree branches.}\label{fig:examples}
 \end{figure}
@@
 A crystal starts with a tiny bit of structure, and that structure is repeated, growing on itself using the same pattern or rule for growth.
-This can be seen quite obviously in objects that are themselves fractals, such as the branching process of trees, but other natural processes follow the rules of fractals.
+This can be seen quite obviously in objects that are themselves fractals, such as the branching process of trees (Figure~\ref{fig:examples}), but other natural processes follow the rules of fractals.
 Hurricanes, avalanches, the diffusion of molecules in solution, the dissolving of porous rock, the electrical breakdown of dialectics, and in the growth of our lungs and brains.
-Strikingly fractal properties can be found in statistical systems or distributions of word usage, foraging behaviors, rock size and in the frequency of scientific journal citations, and network outages of the internet.
-(Wiki, scale invariance) The underlying principle of fractals is that a simple process can through infinitely many iterations to become a very complex process.
+Strikingly fractal properties can be found in statistical systems, distributions of word usage, foraging behaviors, rock size, the frequency of scientific journal citations, and network outages of the internet.
+The underlying principle of fractals is that a simple process can, through infinitely many iterations, become a very complex process.
 Many processes which involve bifurcation, splitting, replication and growth can be fractal mathematics and geometry.
-Fractal mathematics can model these complex systems by searching for the simple rules or laws that drive these processes.
-(\url{http://pages.cs.wisc.edu/~ergreen/honors_thesis/fractal.html})
+Fractal mathematics can model these complex systems by searching for the simple rules or laws that drive these processes (\url{http://pages.cs.wisc.edu/~ergreen/honors_thesis/fractal.html}).
 
@@
 
-Two premiere examples of these mathematical or statistical fractals can be seen in the Koch Curve and the Cantor Set.
+Two premiere examples of these mathematical or statistical fractals can be seen in the Koch Curve and the Cantor Set, seen in Figure~\ref{fig:kochcantor}.
 In each case an image is created by starting with a single line segment and a rule for changing that line segment.
@@
 
-\caption{ }\label{fig:unnamed-chunk-2}
+\caption{Top: Cantor Set. Bottom: Koch Curve.}\label{fig:kochcantor}
 \end{figure}
@@
 There are numerous examples of these types of geometric transformations which result in beautiful and striking constructions.
-Some well known fractal geometries are known as, The Dragon Curve, Sierpinski Triangle, and Hilbert Curve.
+Some well known fractal geometries are known as The Dragon Curve, Sierpinski Triangle, and Hilbert Curve, depicted in Figure~\ref{fig:threees}.
 These examples show the diversity of implementations of fractal properties in geometry.
@@
 
-\caption{ }\label{fig:unnamed-chunk-3}
+\caption{Left to right: Dragon Curve, Sierpinski Triangle, and Hilbert Curve.}\label{fig:threees}
 \end{figure}
@@
 A fractal like the Dragon Curve or Koch Curve can have a dimensionality between 1 and 2, such as 1.2, 1.5, or 1.74823.
-At first this concept feels counter intuitive.
-The non-integer dimensionality occurs because the length of the curve between any two points on the Koch snowflake is effectively infinite.
+At first this concept feels counter-intuitive.
+The non-integer dimensionality occurs because the length of the curve between any two points on the Koch snowflake is effectively infinite (Figure~\ref{fig:snowflake}).
 No small piece of it is line-like, but rather it is composed of an infinite number of segments joined at different angles.
@@
 
-\caption{ }\label{fig:unnamed-chunk-4-1}
+\caption{Koch Snowflake.}\label{fig:snowflake}
 \end{figure}
+
 \begin{figure}
@@
 
-\caption{ }\label{fig:unnamed-chunk-4-2}
+\caption{Fractal with dimensionality between 2 and 3.}\label{fig:cube}
 \end{figure}
@@
 Using fractal mathematics invented by Mandelbrot, we can calculate the dimensionality of any fractal including the Koch and Dragon Curves which have dimensionalities of 1.262 and 1.5236 respectively.
-Similarly an object which begins as a two dimensional fractal, can be iterated to grow into the third dimension and have a calculated dimension between 2 and 3.
+Similarly an object which begins as a two dimensional fractal, can be iterated to grow into the third dimension and have a calculated dimension between 2 and 3 (Figure~\ref{fig:cube}).
 Thus, dimensionality can be considered as the space filling capacity of a fractal.
@@
 Participants select the fractal image they prefer aesthetically and after viewing many pairs with differing dimensions, statistics are used to calculate the most preferred dimensionality range across participants.
-The overarching results of previous research have shown that humans, both adults and children prefer fractals within a range of dimensions that coincide with the fractal dimension that is found in natural objects and scenes, usually between 1.3 and 1.5.Remembering that fractal dimension is an analog for complexity, we can conclude that most humans prefer a moderate level of complexity compared to low or high complexity near the extremes.
-A secondary analysis of fractal fluency has shown that humans often also prefer fractal images to non-fractal images and that we prefer fractals which more closely resemble natural images to fractals which are geometrically exact.
-(Spehar, Clifford, Newell, \& Taylor, 2003) Extensions on these research findings have led to the use of fractal images in therapeutic applications.
-Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (Hagerhall et al., 2015), the reduction of stress using fractal art and architecture (Taylor, 2006) and even in the experience of hearing fractal melodies (Beauvois, 2007).
+The overarching results of previous research have shown that humans, both adults and children prefer fractals within a range of dimensions that coincide with the fractal dimension that is found in natural objects and scenes, usually between 1.3 and 1.5.
+Remembering that fractal dimension is an analog for complexity, we can conclude that most humans prefer a moderate level of complexity compared to low or high complexity near the extremes.
+A secondary analysis of fractal fluency has shown that humans often also prefer fractal images to non-fractal images and that we prefer fractals which more closely resemble natural images to fractals which are geometrically exact (Figure~\ref{fig:natural}, Spehar, Clifford, Newell, \& Taylor, 2003).
+Extensions on these research findings have led to the use of fractal images in therapeutic applications.
+Studies have shown some benefits of experiencing fractals, including physiological responses in EEG measurement of brain activity while viewing fractals (Hagerhall et al., 2015), the reduction of stress using fractal art and architecture (Taylor, 2006), and even in the experience of hearing fractal melodies (Beauvois, 2007).
 There appears to be a clear link between, the fractal's representation of complexity, the connection with natural objects and processes, and the human mind.
@@
 
-\caption{ }\label{fig:unnamed-chunk-5}
+\caption{Fractals that closely resemble natural scenes.}\label{fig:natural}
 \end{figure}
 
-However our natural experience of the world is not so static, fragmented and simple, it is often dynamic, cohesive and alive.
+However, our natural experience of the world is not so static, fragmented, and simple; it is often dynamic, cohesive, and alive.
 To create a more lifelike experience of fractals we present participants with the unfolding process of a fractal as it is iterated through its process of changing in complexity.
@@
 A set of images were generated for each of fourteen different fractal types iterated from 4 to 9 times.
-Each participant viewed a sequential slideshow and a random slideshow.
+Each participant viewed a sequential slideshow and a random slideshow (Figure~\ref{fig:task}).
 Sequential slideshows presented each fractal type through phases of growth and decay from the least complex to most complex iterations and back down from most complex to least complex.
@@
 
-\caption{ }\label{fig:unnamed-chunk-6}
+\caption{Task design.}\label{fig:task}
 \end{figure}
@@
 There was a significant effect of direction on dwell time, \(F(2, 5,565) = 42.68\), \(\mathit{MSE} = 0.36\), \(p < .001\), \(\hat{\eta}^2_G = .015\).
-These results demonstrate that growth conditions showed significantly longer dwell times compared to the decay or random directional conditions.
+Pairwise comparisons revealed that there was a significant difference between growth and decay sequences, \emph{p} \textless{} .001, growth and random sequences, \emph{p} \textless{} .001, and random and decay sequences, \emph{p} \textless{} .001.
+These results demonstrate that participants spent the most time viewing fractals during the growth phase and the least time during the decay phase.
 These results are depicted in Figure~\ref{fig:main}.
@@
 
-In this study a dwell time paradigm which measures looking times of participants as they advance through a self paced slideshow, was used to measure the preferences for fractal images.
+In this study, a dwell time paradigm which measures looking times of participants as they advance through a self paced slideshow was used to measure the preferences for fractal images.
 Slideshows were composed of a variety of different fractal types, each of which was presented in a sequential pattern of growth and decay of complexity.
-Fractal images are abundant in nature, and fractal fluency theory (Taylor, 2006) has shown that humans have evolved perceptual preferences for fractal images.
+Fractal images are abundant in nature, and fractal fluency theory has shown that humans have evolved perceptual preferences for fractal images (Taylor, 2006).
 Previous studies have shown that both adults and children display patterns of aesthetic preference for a particular range of fractal dimension, a mathematical quantification analogous to complexity.
